### 2018-11-22 Visualizations/Draft Visualizations Template.Rmd
Draft Template for Visualization Assignment

---
title: "Draft Visualizationa for Semester Project"
output: html_document
---
#Loading the Data and Necessary Packages
```{r}
library(dplyr)
library(tidyr)
library(ggplot2)
health <- read.csv("mentalsurvey_clean.csv")
```

#Section 1: Showing that Mental and Behavioral Health Issues Impact Workers

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Section 2: What are Other Companies Doing to Assist workers with Mental and Behavioral Health Policies

```{r}

```

#Section 3: What are Factors that Might Limit the Impact of Behavioral Health Outreach

##Anonymity Policies

If employees feel that their anonymity is not protected, they may be less likely to reach out for help.

###Anonymity Policies by Company Size

```{r}

```

###Anonymity Policies by Whether it is a Tech Company

```{r}

```

##Ease of Asking for Leave For A Mental Health Issue

This is important because if employees feel that asking for time off from work for medical leave, they may be less likely to seek the help they need.

###Answers by Gender

```{r}
#Crosstab table
ELDbG <- table(health$If.a.mental.health.issue.prompted.you.to.request.a.medical.leave.from.work..asking.for.that.leave.would.be., health$gender)
ELDbG
```

####Chi-Squared

We get a warning that the approximation may be incorrect, likely because some of the values from the table are small.  However, it potentially indicates that that the differences between genders may not be statistically significant (or we do not have enough information)

```{r}
chisq.test(ELDbG)
```

###Answers by Age Group

```{r}
#Do the AgeGroup Variable
labs <- c(paste(seq(17, 74, by = 20), seq(37, 80, by = 20),
                sep = "-"))
health$AgeGroup <- cut(health$age, breaks = c(seq(17, 74, by = 20), Inf), labels = labs, right = FALSE)
```

```{r}
#Crosstab table
ELDbA <- table(health$If.a.mental.health.issue.prompted.you.to.request.a.medical.leave.from.work..asking.for.that.leave.would.be., health$AgeGroup)
ELDbA
```

We get a warning that the approximation may be incorrect, likely because some of the values from the table are small.  However, it potentially indicates that that the differences between age groups may not be statistically significant (or we do not have enough information)

###Chi-Squared
```{r}
chisq.test(ELDbA)
```

###Answers by Company Size

```{r}
#Put company size in order
ENumOrder  = factor(health$How.many.employees.does.your.company.or.organization.have, levels=c("1-5", "6-25", "26-100", "100-500", "500-1000", "More than 1000"))
```

```{r}
#Crosstab table
ELDbCS <- table(health$If.a.mental.health.issue.prompted.you.to.request.a.medical.leave.from.work..asking.for.that.leave.would.be., ENumOrder)
ELDbCS
```

###Chi-Squared

```{r}
chisq.test(ELDbCS)
```

###Answers by Whether Company is Primarily a Tech Company

```{r}

```

####Chi-Squared

```{r}

```

###Answers by Whether Anonymity Is Protected

```{r}

```

####Chi-Squared

```{r}

```

###Answers by Whether Current Company Provides Mental Health Benefits

```{r}
#Crosstab Table
ELDbMHB <- table(health$If.a.mental.health.issue.prompted.you.to.request.a.medical.leave.from.work..asking.for.that.leave.would.be., health$Does.your.employer.provide.mental.health.benefits.as.part.of.healthcare.coverage.)
ELDbMHB
```

###Chi-Squared

```{r}
chisq.test(ELDbMHB)
```

###Answers by Whether Current Company Has Ever Formally Discussed Mental Health

```{r}
ELDbEDM <- table(health$If.a.mental.health.issue.prompted.you.to.request.a.medical.leave.from.work..asking.for.that.leave.would.be., health$Has.your.employer.ever.formally.discussed.mental.health..for.example..as.part.of.a.wellness.campaign.or.other.official.communication..)
ELDbEDM
```

####Chi-Squared

```{r}
chisq.test(ELDbEDM)
```

###Answers by Whether Current Company Offers Other Resources

```{r}
ELDbEOR <- table(health$If.a.mental.health.issue.prompted.you.to.request.a.medical.leave.from.work..asking.for.that.leave.would.be., health$Does.your.employer.offer.resources.to.learn.more.about.mental.health.concerns.and.options.for.seeking.help.)
ELDbEOR
```

####Chi-Squared

```{r}
chisq.test(ELDbEOR)
```

###Answers by If They Ever Saw A Poor Response to Mental Health Issue

```{r}
ELDbPR <- table(health$If.a.mental.health.issue.prompted.you.to.request.a.medical.leave.from.work..asking.for.that.leave.would.be., health$Have.you.observed.or.experienced.an.unsupportive.or.badly.handled.response.to.a.mental.health.issue.in.your.current.or.previous.workplace.)
ELDbPR
```

####Chi-Squared
```{r}
chisq.test(ELDbPR)
```

##Comfort with talking to Supervisor About Mental Health

This is important because if an employee has a mental health issue, they should ideally be comfortable discussing it with a supervisor in case they need additional assistance. In addition, we may want to consider training supervisors on how to handle instances where employees reach out to them about mental health.

###Answers by Gender

```{r}
MHbG <- table(health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.direct.supervisor.s.., health$gender)
MHbG
```

####Chi-Squared

```{r}
chisq.test(MHbG)
```

###Answers by Age Group

```{r}
MHbA <- table(health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.direct.supervisor.s.., health$AgeGroup)
MHbA
```

####Chi-Squared

```{r}
chisq.test(MHbA)
```

###Answers by Company Size
```{r}
MHbCS <- table(health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.direct.supervisor.s.., ENumOrder)
MHbCS
```

####Chi-Squared
```{r}
chisq.test(MHbCS)
```

###Answers by Whether Company is Primarily a Tech Company

```{r}

```

###Answers by Whether Anonymity Is Protected

```{r}

```

###Answers by Whether Current Company Provides Mental Health Benefits

```{r}
MHbMHB <- table(health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.direct.supervisor.s.., health$Does.your.employer.provide.mental.health.benefits.as.part.of.healthcare.coverage.)
MHbMHB
```

####Chi-Squared
```{r}
chisq.test(MHbMHB)
```

###Answers by Whether Current Company Has Ever Formally Discussed Mental Health

```{r}
MHbEDM <- table(health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.direct.supervisor.s.., health$Has.your.employer.ever.formally.discussed.mental.health..for.example..as.part.of.a.wellness.campaign.or.other.official.communication..)
MHbEDM
```

####Chi-Squared

```{r}
chisq.test(MHbEDM)
```

###Answers by Whether Current Company Offers Other Resources

```{r}
MHbEOR <- table(health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.direct.supervisor.s.., health$Does.your.employer.offer.resources.to.learn.more.about.mental.health.concerns.and.options.for.seeking.help.)
MHbEOR
```

####Chi-Squared

```{r}
chisq.test(MHbEOR)
```

###Answers by If They Ever Saw A Poor Response to Mental Health Issue

```{r}
MHbPR <- table(health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.direct.supervisor.s.., health$Have.you.observed.or.experienced.an.unsupportive.or.badly.handled.response.to.a.mental.health.issue.in.your.current.or.previous.workplace.)
MHbPR
```

####Chi-Squared

```{r}
chisq.test(MHbPR)
```

###Answers by If They Think Supervisor Would View Them Negatively If They Knew You Suffered From a Mental Health Issue

```{r}

```

##Comfort with taking to Coworkers About Mental Health

This is important because if an employee has a mental health issue, they should ideally be comfortable discussing it with a coworkers in case they need additional assistance. In addition, we may want to consider training employees on how to handle instances where coworkers reach out to them about mental health.

###Answers by Gender

```{r}
MHCbG <- table(health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.coworkers., health$gender)
MHCbG
```

####Chi-Squared

```{r}
chisq.test(MHCbG)
```

###Answers by Age Group

```{r}
MHCbA <- table(health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.coworkers., health$AgeGroup)
MHCbA
#Proportions (as column percentages)
prop.table(MHCbA, 2)
#Chi-Squared (We get a big chi-quared and a warning it may be incorrect, likely b/c small values for the 57-77 column)
chisq.test(MHCbA)
```

###Answers by Company Size

```{r}
MHCbCS <- table(health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.coworkers., ENumOrder)
MHCbCS
#Proportions (as column percentages)
prop.table(MHCbCS, 2)
#Chi-Squared (the p value is small)
chisq.test(MHCbCS)
```

###Answers by Whether Company is Primarily a Tech Company

```{r}

```

###Answers by Whether Anonymity Is Protected

```{r}

```

###Answers by Whether Current Company Provides Mental Health Benefits

```{r}
MHCbMHB <- table(health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.coworkers., health$Does.your.employer.provide.mental.health.benefits.as.part.of.healthcare.coverage.)
MHCbMHB
```

####Chi-Squared

```{r}
chisq.test(MHCbMHB)
```

###Answers by Whether Current Company Has Ever Formally Discussed Mental Health

```{r}
MHCbEDM <- table(health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.coworkers., health$Has.your.employer.ever.formally.discussed.mental.health..for.example..as.part.of.a.wellness.campaign.or.other.official.communication..)
MHCbEDM
```

####Chi-Squared
```{r}
chisq.test(MHCbEDM)
```

###Answers by Whether Current Company Offers Other Resources

```{r}
MHCbEOR <- table(health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.coworkers., health$Does.your.employer.offer.resources.to.learn.more.about.mental.health.concerns.and.options.for.seeking.help.)
MHCbEOR
```

####Chi-Squared

```{r}
chisq.test(MHCbEOR)
```

###Answers by If They Ever Saw A Poor Response to Mental Health Issue

```{r}
MHCbPR <- table(health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.coworkers., health$Have.you.observed.or.experienced.an.unsupportive.or.badly.handled.response.to.a.mental.health.issue.in.your.current.or.previous.workplace.)
MHCbPR
```

####Chi-Squared

```{r}
chisq.test(MHCbPR)
```

###Answers by If They Think Coworkers Would View Them Negatively If They Knew You Suffered From a Mental Health Issue

```{r}
MHCbCN <- table(health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.coworkers., health$Do.you.think.that.team.members.co.workers.would.view.you.more.negatively.if.they.knew.you.suffered.from.a.mental.health.issue.)
MHCbCN
```

####Chi-Squared
```{r}
chisq.test(MHCbCN)
```

### 2018-11-25 Visualizations/Laura R Code.R
Delete Laura R Code.R

@@ -1,214 +1,0 @@
-mental <- read.csv("mentalsurvey_clean.csv")
-
-#Do a table showing answers to question: "How many employees does your company or organization have"
-table(mental$How.many.employees.does.your.company.or.organization.have)
-
-#Do a table showing answers to question: "How willing would you be to share with friends and family that you have a mental illness?"
-table(mental$How.willing.would.you.be.to.share.with.friends.and.family.that.you.have.a.mental.illness.)
-#Do a barplot showing answers to question: ""How willing would you be to share with friends and family that you have a mental illness?"
-barplot(table(mental$How.willing.would.you.be.to.share.with.friends.and.family.that.you.have.a.mental.illness.), main = "Willingness to share mental illness with friends and family", names.arg=c("Neutral", "N/A (no mental illness", "Not Open", "Somewhat not open", "Somewhat open", "Very Open"), xlab = "Answer", ylab = "Count", ylim=c(0,600), las = 1, cex.names=0.5)
-
-#Do a table showing answers to question: "Has your employer ever formally discussed mental health (for example, as part of a wellness campaign or other official communication)?"
-table(mental$Has.your.employer.ever.formally.discussed.mental.health..for.example..as.part.of.a.wellness.campaign.or.other.official.communication..)
-#Do a barplot showing answers to question: "Has your employer ever formally discussed mental health (for example, as part of a wellness campaign or other official communication)?"
-barplot(table(mental$Has.your.employer.ever.formally.discussed.mental.health..for.example..as.part.of.a.wellness.campaign.or.other.official.communication..), main = "Has your employer formally discussed mental health with you?", xlab = "Answer", ylab = "Count", ylim=c(0,1000))
-
-#Do a table showing answers to question: "Is your anonymity protected if you choose to take advantage of mental health or substance abuse treatment resources provided by your employer?"
-table(mental$Is.your.anonymity.protected.if.you.choose.to.take.advantage.of.mental.health.or.substance.abuse.treatment.resources.provided.by.your.employer.)
[…]

### 2018-11-25 Visualizations/Draft Visualizations Template.Rmd

@@
 library(ggplot2)
+#Insert the location of your data here, for example
 health <- read.csv("mentalsurvey_clean.csv")
@@
 
+####Crosstab Table
+
 ```{r}
+#Put company size in order
+CompanySize  = factor(health$How.many.employees.does.your.company.or.organization.have, levels=c("1-5", "6-25", "26-100", "100-500", "500-1000", "More than 1000"))
+#Create Cross-tab Table
+APbCS <- table(health$Is.your.anonymity.protected.if.you.choose.to.take.advantage.of.mental.health.or.substance.abuse.treatment.resources.provided.by.your.employer., CompanySize)
+head(APbCS)
+```
 
+####Proportions table
+
+```{r}
+#Create a proportions table by Row
+prop.table(APbCS, 2)
 ```
+
+####Chi-Squared Test
+
+```{r}
+#Do a chi-squared test
+chisq.test(APbCS)
+```
+
+####Visualization of Data
+
+```{r}
+ggplot(health, aes(CompanySize, health$Is.your.anonymity.protected.if.you.choose.to.take.advantage.of.mental.health.or.substance.abuse.treatment.resources.provided.by.your.employer.)) + geom_jitter(height = .3, width = .3) + ggtitle("Anonymity Protections For Mental Health Services") + xlab("Company Size") + ylab("Is Anonymity Protected?")
+```
+
+####Interpretation of Results
+
+The table and chart above show that across all company sizes, most respondents indicate that they do not know what their current company's anonymity policy is towards those using mental health services.
+For companies of 1-5 employees, the next most common answer is "No" (anonymity is not protected).
+However, for companies larger than 5 employees, the results appear fairly consistent, with the majority of respondents (60-70 percent) indicating that they do not know anonymity policies, a sizable minority of respondents saying that anonymity is protected (25-32 percent), and less than 10 percent of respondents in each group saying anonymity is not protected.
+Based off of the chi-squared test, it is not clear if there is a statistically significant difference in anonymity policies of companies of different sizes.
 
@@
 
+####Cross-tab Table
+
 ```{r}
+#Add labels to tech company org
+TLabel <- factor(health$Is.your.employer.primarily.a.tech.company.organization.,
+levels = c(0, 1),
+labels = c("No", "Yes"))
+#Create a crosstab table
+APbT2 <- table(health$Is.your.anonymity.protected.if.you.choose.to.take.advantage.of.mental.health.or.substance.abuse.treatment.resources.provided.by.your.employer., TLabel)
+head(APbT2)
+```
 
+####Proportions table
+
+```{r}
+#Create a proportions table by Row
+prop.table(APbT2, 2)
 ```
+
+####Chi-Squared Test
+
+```{r}
+#Do a chi-squared test
+chisq.test(APbT2)
+```
+
+####Visualization of Data
+
+OPTION 1
+
+```{r}
+ggplot(health, aes(TLabel, health$Is.your.anonymity.protected.if.you.choose.to.take.advantage.of.mental.health.or.substance.abuse.treatment.resources.provided.by.your.employer.)) + geom_jitter(height = .3, width = .3) + ggtitle("Anonymity Protections For Tech vs.
+Non-Tech Companies") + xlab("Is Employer Primarily Tech?") + ylab("Is Anonymity Protected?")
+```
+
+OPTION 2
+
+```{r}
+#Run Counts
+summary(health$Is.your.anonymity.protected.if.you.choose.to.take.advantage.of.mental.health.or.substance.abuse.treatment.resources.provided.by.your.employer.)
+#Modify Labels
+levels(health$Is.your.anonymity.protected.if.you.choose.to.take.advantage.of.mental.health.or.substance.abuse.treatment.resources.provided.by.your.employer.) <- c("Don't Know Anonymity Policy", "Anonymity Not Protected", "Anonymity Protected")
+#Check to make sure
+summary(health$Is.your.anonymity.protected.if.you.choose.to.take.advantage.of.mental.health.or.substance.abuse.treatment.resources.provided.by.your.employer.)
+```
+
+```{r}
+#Create Visualization
+p3 <- ggplot(health, aes(x = TLabel))+geom_bar()+facet_wrap(~ health$Is.your.anonymity.protected.if.you.choose.to.take.advantage.of.mental.health.or.substance.abuse.treatment.resources.provided.by.your.employer.)+ ggtitle("Anonymity Protections For Tech vs.
+Non-Tech Companies") + xlab("Is Employer Primarily Tech?") + ylab("Count")
+p3
+```
+
+####Interpretation of Results
+
+The difference between primarily tech and non-primarily tech companies is not statistically significant in regards to anonymity policies for those seeking mental health services.
+In both cases, the clear majority of those surveyed indicated that they do not know  their current company's anonymity policy is towards those using mental health services.
+In both cases, the next most common response to the question is that anonymity is protected for those using mental health services.
 
@@
 ###Answers by Company Size
-
-```{r}
-#Put company size in order
-ENumOrder  = factor(health$How.many.employees.does.your.company.or.organization.have, levels=c("1-5", "6-25", "26-100", "100-500", "500-1000", "More than 1000"))
-```
 

### 2018-11-25 Visualizations/Draft Visualizations Template.Rmd
update template
I updated the template with my analyses.  I also added the csv file because otherwise, we would have to work of different files on our machines and it has been causing problems.  I am also uploading a sample of what the output was on the markdown file.

--- 2018-11-22 Visualizations/Draft Visualizations Template.Rmd
@@
 title: "Draft Visualizationa for Semester Project"
-output: html_document
+output: word_document
 ---
+
 #Loading the Data and Necessary Packages
@@
 
+####Crosstab Table
+
 ```{r}
+#Put company size in order
+health$CompanySize  = factor(health$How.many.employees.does.your.company.or.organization.have, levels=c("1-5", "6-25", "26-100", "100-500", "500-1000", "More than 1000"))
+#Create Cross-tab Table
+APbCS <- table(health$Is.your.anonymity.protected.if.you.choose.to.take.advantage.of.mental.health.or.substance.abuse.treatment.resources.provided.by.your.employer., health$CompanySize)
+head(APbCS)
+```
 
+####Proportions table
+
+```{r}
+#Create a proportions table by Row
+prop.table(APbCS, 2)
 ```
+
+####Chi-Squared Test
+
+```{r}
+#Do a chi-squared test
+chisq.test(APbCS)
+```
+
+####Visualization of Data
+
+```{r}
+t0 <- ggplot(health, aes(x = health$Is.your.anonymity.protected.if.you.choose.to.take.advantage.of.mental.health.or.substance.abuse.treatment.resources.provided.by.your.employer.))+geom_bar()+facet_wrap(~health$CompanySize, scales="free_y") + ggtitle("Perceived Difficulty of Asking for Leave by Gender") + xlab("Perceived Difficulty Level") + ylab("Count")
+t0
+```
+
+####Interpretation of Results
+
+The table and chart above show that across all company sizes, most respondents indicate that they do not know what their current company's anonymity policy is towards those using mental health services.
+For companies of 1-5 employees, the next most common answer is "No" (anonymity is not protected).
+However, for companies larger than 5 employees, the results appear fairly consistent, with the majority of respondents (60-70 percent) indicating that they do not know anonymity policies, a sizable minority of respondents saying that anonymity is protected (25-32 percent), and less than 10 percent of respondents in each group saying anonymity is not protected.
+Based off of the chi-squared test, it is not clear if there is a statistically significant difference in anonymity policies of companies of different sizes.
+However, the fact that the majority of respondents across company sizes do not know their company's anonymity policy is something that has to be addressed, as a study by Milne, et al (1994) has found that participants tended to be more confident in a company's Employee Assistance Program if they felt it was confidential (p.
+141).
+Therefore, any outreach must make the company's anonymity policy clear.
 
@@
 
+####Cross-tab Table
+
 ```{r}
+#Add labels to tech company org
+TLabel <- factor(health$Is.your.employer.primarily.a.tech.company.organization.,
+levels = c(0, 1),
+labels = c("No", "Yes"))
+#Create a crosstab table
+APbT2 <- table(health$Is.your.anonymity.protected.if.you.choose.to.take.advantage.of.mental.health.or.substance.abuse.treatment.resources.provided.by.your.employer., TLabel)
+head(APbT2)
+```
 
+####Proportions table
+
+```{r}
+#Create a proportions table by Row
+prop.table(APbT2, 2)
 ```
+
+####Chi-Squared Test
+
+```{r}
+#Do a chi-squared test
+chisq.test(APbT2)
+```
+
+####Visualization of Data
+
+```{r}
+#Create Labels for Tech Companies
+techlabel <- c(
+`0` = "Not Primarily a Tech Company",
+`1` = "Primarily a Tech Company")
+#Create Visualization
+t1 <- ggplot(health, aes(x = health$Is.your.anonymity.protected.if.you.choose.to.take.advantage.of.mental.health.or.substance.abuse.treatment.resources.provided.by.your.employer.))+geom_bar()+facet_wrap(health$Is.your.employer.primarily.a.tech.company.organization.
+~ ., labeller = as_labeller(techlabel)) + ggtitle("Anonymity Protections For Tech vs.
+Non-Tech Companies") + xlab("Is your anonymity protected?") + ylab("Count")
+t1
+```
+
+####Interpretation of Results
+
+The difference between primarily tech and non-primarily tech companies is not statistically significant in regards to anonymity policies for those seeking mental health services.
+However, this may be influenced by the fact that the majority of those surveyed work for primiarily tech-oriented companies, so we do not have a large sample of those working for non-tech companies.
+Furthermore, we do not know the industry that these non-tech companies are in, which means we cannot draw any firm conclusions here.
+Nevertheless, in both cases, the clear majority of those surveyed indicated that they do not know  their current company's anonymity policy is towards those using mental health services.
+In both cases, the next most common response to the question is that anonymity is protected for those using mental health services.
+As described above, the fact the majority of respondents do not know their company's anonymity policy is something that has to be addressed.
 
@@
 ```{r}
+#Modify Labels
+pd2 <- factor(health$If.a.mental.health.issue.prompted.you.to.request.a.medical.leave.from.work..asking.for.that.leave.would.be.,
+levels = c("Very easy", "Somewhat easy", "Neither easy nor difficult","Somewhat difficult", "Very difficult", "I don't know"),
+labels = c("V Easy", "S Easy", "Neutral", "SW Hard", "V Hard", "Don't Know"))
+```
+
+```{r}
 #Crosstab table
-ELDbG <- table(health$If.a.mental.health.issue.prompted.you.to.request.a.medical.leave.from.work..asking.for.that.leave.would.be., health$gender)
+ELDbG <- table(pd2, health$gender)
 ELDbG
+prop.table(ELDbG, 2)
 ```
@@
 ```
+
+####Visualization of Data
+
+```{r}
+#Create Visualization
+t2 <- ggplot(health, aes(x = pd2))+geom_bar()+facet_grid(health$gender ~ ., scales="free_y") + ggtitle("Perceived Difficulty of Asking for Leave by Gender") + xlab("Perceived Difficulty Level") + ylab("Count")
+t2
+```
+
+####Interpretation of Results
+
+Across all genders, the most common answer is "Somewhat Easy".
+Interestingly, for women the second most common answer is "Somewhat Difficult", while for men the second most common answer is "Very Easy."  For those indicating their gender falls into another category, an equal amount indicated that they felt asking for leave was very hard or provided a neutral response ("neither easy or hard").
+Across all genders there is a significant group of people indicating they find it somewhat to very hard to ask for leave.
+That being said, there are fewer women and those from other genders participating in this survey (compared to men), which may impact our results.
+Furthermore, the chi-squared test indicated that the approximation may be incorrect, likely because some of the values from the table are small.
 
@@
 #Crosstab table
-ELDbA <- table(health$If.a.mental.health.issue.prompted.you.to.request.a.medical.leave.from.work..asking.for.that.leave.would.be., health$AgeGroup)
+ELDbA <- table(pd2, health$AgeGroup)
 ELDbA
+#Proportions table
+prop.table(ELDbA)
+```
+
+####Chi-Squared
+
+```{r}
+chisq.test(ELDbA)
 ```
@@
 
-###Chi-Squared
+####Visualization of Data
+
 ```{r}
-chisq.test(ELDbA)
+#Create Visualization
+t3 <- ggplot(health, aes(x = pd2))+geom_bar()+facet_grid(health$AgeGroup ~ ., scales="free_y") + ggtitle("Perceived Difficulty of Asking for Leave by Age Group") + xlab("Perceived Difficulty Level") + ylab("Count")
+t3
 ```
+
+####Interpretation of Results
+
+The most common response for those in the 17-27 and 37-57 age ranges is that asking for leave for a mental health issue was "Somewhat Easy" and the second most common isthat asking for leave "Very Easy".
+However, there is a significant number in both age groups who provided a neutral answer (e.g., neither easy or difficult) or indicated that they felt asking for leave was hard/very hard.
+That being said, there are few people who are 57-77 participating in this survey and there are fewer people in the 37-57 age group than the 17-27 age group.
+Furthermore, the chi-squared test indicated that the approximation may be incorrect, likely because some of the values from the table are small (since few people fell into the 57-77 age range).
 
@@
 ```{r}
-#Put company size in order
-ENumOrder  = factor(health$How.many.employees.does.your.company.or.organization.have, levels=c("1-5", "6-25", "26-100", "100-500", "500-1000", "More than 1000"))
+#Crosstab table
+ELDbCS <- table(pd2, health$CompanySize)
+ELDbCS
+prop.table(ELDbCS, 2)
 ```
 
-```{r}
-#Crosstab table
-ELDbCS <- table(health$If.a.mental.health.issue.prompted.you.to.request.a.medical.leave.from.work..asking.for.that.leave.would.be., ENumOrder)
-ELDbCS
-```
+####Chi-Squared
 
-###Chi-Squared
+Since the p value is less than .01, then we can say that there may be a significant difference in the answers to perceived ease for requesting leave by different company size groups.
 
@@
 
-###Answers by Whether Company is Primarily a Tech Company
+####Visualization of Data
 
 ```{r}
+#Modify Labels
+pd3 <- factor(health$If.a.mental.health.issue.prompted.you.to.request.a.medical.leave.from.work..asking.for.that.leave.would.be.,
+levels = c("Very easy", "Somewhat easy", "Neither easy nor difficult","Somewhat difficult", "Very difficult", "I don't know"),
+labels = c("E", "SE", "N", "SH", "H", "D"))
+#Create Visualization
+t4 <- ggplot(health, aes(x = pd3))+geom_bar()+facet_grid(~ health$CompanySize) + ggtitle("Perceived Difficulty of Asking for Leave by Company Size") + xlab("Perceived Difficulty Level") + ylab("Count")
+t4
+```
 
+NOTE:  E = Very Easy, S = Somewhat Easy, N = Neutral (or Neither Easy nor Difficult), SH = Somewhat Hard, H = Very Hard, D = Don't Know.
+
+####Interpretation of Results
+
+For very small companies (1-5 employees), there seems to be a fairly even split between those who perceive taking leave for mental health to be easy and those who perceive it to be hard.
+For other small companies (6-25 employees), approximately the same number of people say that it is easy/somewhat easy or provide a neutral response.
+However, in this case, the most common answer is that they would perceive it as somehwat hard to ask for leave.
+For larger companies, the most common answer is that they perceive it to be somewhat easy to request leave for a mental illness.
+Therefore it appears that as the company size gets larger, it may be perceived as easier in most companies to request leave related to a mental illness.
+However, there is still sizable minority of employees who work for larger companies (over 25 employees) who do perceive it as hard or very hard to ask for leave.
+Therefore, a lot may vary by the company.
+
+###Answers by Whether Current Company Provides Mental Health Benefits
+
+```{r}
+#Modify Labels
+health$mhb2 <- factor(health$Does.your.employer.provide.mental.health.benefits.as.part.of.healthcare.coverage.,
+levels = c("I don't know", "No", "Not eligible for coverage / N/A","Yes"),
+labels = c("Don't Know", "No", "Ineligible/NA", "Yes"))
+#Crosstab Table
+ELDbMHB <- table(pd2, health$mhb2)
+ELDbMHB
 ```
@@
 
-```{r}
-
-```
-
-###Answers by Whether Anonymity Is Protected
-
-```{r}
-
-```
-
-####Chi-Squared
-
-```{r}
-
-```
-
-###Answers by Whether Current Company Provides Mental Health Benefits
-
-```{r}
-#Crosstab Table
-ELDbMHB <- table(health$If.a.mental.health.issue.prompted.you.to.request.a.medical.leave.from.work..asking.for.that.leave.would.be., health$Does.your.employer.provide.mental.health.benefits.as.part.of.healthcare.coverage.)
-ELDbMHB
-```
-
-###Chi-Squared
+Because the p value is not less than .01 we do not reject the null (there are no differences between categories).
 
@@
 
+####Create Visualization
+
+```{r}
+t5 <- ggplot(health, aes(x = pd3))+geom_bar()+facet_grid(~ health$mhb2, scales="free_y") + ggtitle("Perceived Difficulty of Asking for Leave by MH Benefit Provision") + xlab("Perceived Difficulty Level") + ylab("Count")
+t5
+```
+NOTE:  E = Very Easy, S = Somewhat Easy, N = Neutral (or Neither Easy nor Difficult), SH = Somewhat Hard, H = Very Hard, D = Don't Know.
+
 ###Answers by Whether Current Company Has Ever Formally Discussed Mental Health
@@
 ```{r}
-ELDbEDM <- table(health$If.a.mental.health.issue.prompted.you.to.request.a.medical.leave.from.work..asking.for.that.leave.would.be., health$Has.your.employer.ever.formally.discussed.mental.health..for.example..as.part.of.a.wellness.campaign.or.other.official.communication..)
+ELDbEDM <- table(pd2, health$Has.your.employer.ever.formally.discussed.mental.health..for.example..as.part.of.a.wellness.campaign.or.other.official.communication..)
 ELDbEDM
@@
 
+Because the p value is less than .01 we can reject the null and say that we think that there are differences between categories.
+
 ```{r}
@@
 
+####Create Visualization
+
+```{r}
+t6 <- ggplot(health, aes(x = pd2))+geom_bar()+facet_grid( health$Has.your.employer.ever.formally.discussed.mental.health..for.example..as.part.of.a.wellness.campaign.or.other.official.communication..
+~., scales="free_y") + ggtitle("Perceived Difficulty of Asking for Leave by MH Discussion by Employer") + xlab("Perceived Difficulty Level") + ylab("Count")
+t6
+```
+
+####Interpretation of Results
+
+Across all categories (e.g., yes they have discussed, no they haven't, don't know), the most common response is that most recipients think it would be somewhat easy to request leave.
+Interestingly, for those who did not know if there has been a discussion, a large contingent also indicated they don't know how hard it would be to request leave.
+For those where there has been a discussion, far fewer people say it would be hard to request leave to handle a mental illness than those who say it would be easy to very easy.
+For those where there has not been a discussion (which is the majority of respondents), the second most common answer is that it would be somewhat hard to request leave to hanlde a mental illness.
+
 ###Answers by Whether Current Company Offers Other Resources
@@
 ```{r}
-ELDbEOR <- table(health$If.a.mental.health.issue.prompted.you.to.request.a.medical.leave.from.work..asking.for.that.leave.would.be., health$Does.your.employer.offer.resources.to.learn.more.about.mental.health.concerns.and.options.for.seeking.help.)
+ELDbEOR <- table(pd2, health$Does.your.employer.offer.resources.to.learn.more.about.mental.health.concerns.and.options.for.seeking.help.)
 ELDbEOR
@@
 
+####Create Visualization
+
+```{r}
+t7 <- ggplot(health, aes(x = pd2))+geom_bar()+facet_grid( health$Does.your.employer.offer.resources.to.learn.more.about.mental.health.concerns.and.options.for.seeking.help.
+~., scales="free_y") + ggtitle("Perceived Difficulty of Asking for Leave by Mental Health Resource Provision") + xlab("Perceived Difficulty Level") + ylab("Count")
+t7
+```
+
+####Interpretation of Results
+
+Across all categories (e.g., yes there are resources, no they aren't, don't know), the most common response is that most recipients think it would be somewhat easy to request leave.
+Similarly to the results provided above, in companies where there are other resources provided, fewer people say it would be hard to request leave to handle a mental illness than those who say it would be easy to very easy.
+For those where there are not additional resources offered related to mental health (the majority of respondents), the second most common answer is that it would be somewhat hard to request leave to hanlde a mental illness.
+
 ###Answers by If They Ever Saw A Poor Response to Mental Health Issue
@@
 ```{r}
-ELDbPR <- table(health$If.a.mental.health.issue.prompted.you.to.request.a.medical.leave.from.work..asking.for.that.leave.would.be., health$Have.you.observed.or.experienced.an.unsupportive.or.badly.handled.response.to.a.mental.health.issue.in.your.current.or.previous.workplace.)
+ELDbPR <- table(pd2, health$Have.you.observed.or.experienced.an.unsupportive.or.badly.handled.response.to.a.mental.health.issue.in.your.current.or.previous.workplace.)
 ELDbPR
+prop.table(ELDbPR, 2)
+```
+
+#Revise Labels
+
+```{r}
+#Modify Labels
+health$epr <- factor(health$Have.you.observed.or.experienced.an.unsupportive.or.badly.handled.response.to.a.mental.health.issue.in.your.current.or.previous.workplace.,
+levels = c("Maybe/Not sure", "N/A", "No","Yes, I experienced", "Yes, I observed"),
+labels = c("Don't Know", "N/A", "No", "Yes, experienced", "Yes, observed"))
+table(pd2, health$epr)
 ```
@@
 ####Chi-Squared
+
+Because the p value is less than .01 we can reject the null and say that we think that there are differences between categories.
+
 ```{r}
@@
 ```
+
+####Create Visualization
+
+```{r}
+t8 <- ggplot(health, aes(x = pd3))+geom_bar()+facet_grid(~ health$epr) + ggtitle("Perceived Difficulty of Asking for Leave by Exp.
+with Poor MH Response") + xlab("Perceived Difficulty Level") + ylab("Count")
+t8
+```
+NOTE:  E = Very Easy, S = Somewhat Easy, N = Neutral (or Neither Easy nor Difficult), SH = Somewhat Hard, H = Very Hard, D = Don't Know.
+
+####Interpretation of Results
+
+Most people surveyed indicate that they have never had an experience with an unsupportive or badly handled response to mental health in the workplace.
+Among those who selected this response, the vast majority indicate they think that it would be very or somewhat easy to request leave to handle a mental illness.
+For those who have observed a badly handled response, the most common response is that they would find it somewhat easy to request leave, but the second most common is that it they would find it somewhat difficult.
+For those who have experienced a poorly handled response, the most common response is that they would find it somewhat easy to request leave, but a significant amount said they would find it hard or very hard to request leave (or provided a neutral response saying it would be neither easy or difficult).
+Therefore, it is possible that experience with a poorly handled response may have an impact on perceived ease of requesting leave.
 
@@
 ```{r}
-MHbCS <- table(health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.direct.supervisor.s.., ENumOrder)
+MHbCS <- table(health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.direct.supervisor.s.., health$CompanySize)
 MHbCS
@@
 chisq.test(MHbCS)
-```
-
-###Answers by Whether Company is Primarily a Tech Company
-
-```{r}
-
-```
-
-###Answers by Whether Anonymity Is Protected
-
-```{r}
-
-```
-
-###Answers by Whether Current Company Provides Mental Health Benefits
-
-```{r}
-MHbMHB <- table(health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.direct.supervisor.s.., health$Does.your.employer.provide.mental.health.benefits.as.part.of.healthcare.coverage.)
-MHbMHB
-```
-
-####Chi-Squared
-```{r}
-chisq.test(MHbMHB)
-```
-
-###Answers by Whether Current Company Has Ever Formally Discussed Mental Health
-
-```{r}
-MHbEDM <- table(health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.direct.supervisor.s.., health$Has.your.employer.ever.formally.discussed.mental.health..for.example..as.part.of.a.wellness.campaign.or.other.official.communication..)
-MHbEDM
-```
-
-####Chi-Squared
-
-```{r}
-chisq.test(MHbEDM)
-```
-
-###Answers by Whether Current Company Offers Other Resources
-
-```{r}
-MHbEOR <- table(health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.direct.supervisor.s.., health$Does.your.employer.offer.resources.to.learn.more.about.mental.health.concerns.and.options.for.seeking.help.)
-MHbEOR
-```
-
-####Chi-Squared
-
-```{r}
-chisq.test(MHbEOR)
 ```
@@
 ```{r}
-MHCbCS <- table(health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.coworkers., ENumOrder)
+MHCbCS <- table(health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.coworkers., health$CompanySize)
 MHCbCS
@@
 chisq.test(MHCbCS)
-```
-
-###Answers by Whether Company is Primarily a Tech Company
-
-```{r}
-
-```
-
-###Answers by Whether Anonymity Is Protected
-
-```{r}
-
-```
-
-###Answers by Whether Current Company Provides Mental Health Benefits
-
-```{r}
-MHCbMHB <- table(health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.coworkers., health$Does.your.employer.provide.mental.health.benefits.as.part.of.healthcare.coverage.)
-MHCbMHB
-```
-
-####Chi-Squared
-
-```{r}
-chisq.test(MHCbMHB)
-```
-
-###Answers by Whether Current Company Has Ever Formally Discussed Mental Health
-
-```{r}
-MHCbEDM <- table(health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.coworkers., health$Has.your.employer.ever.formally.discussed.mental.health..for.example..as.part.of.a.wellness.campaign.or.other.official.communication..)
-MHCbEDM
-```
-
-####Chi-Squared
-```{r}
-chisq.test(MHCbEDM)
-```
-
-###Answers by Whether Current Company Offers Other Resources
-
-```{r}
-MHCbEOR <- table(health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.coworkers., health$Does.your.employer.offer.resources.to.learn.more.about.mental.health.concerns.and.options.for.seeking.help.)
-MHCbEOR
-```
-
-####Chi-Squared
-
-```{r}
-chisq.test(MHCbEOR)
 ```
@@
 ```
+
+#Works Cited
+
+Milne, S.
+H., Blum, T.
+C., & Roman, P.
+M.
+(1994).
+Factors Influencing Employees’ Propensity to Use an Employee Assistance Program.
+Personnel Psychology, 47(1), 123–145.
+Retrieved October 24, 2018 from http://search.ebscohost.com.proxy-um.researchport.umd.edu/login.aspx?direct=true&db=bth&AN=9411113184&site=ehost-live

### 2018-11-26 Visualizations/Draft Visualizations Template.Rmd
Update visualizations
Added more of my analysis visualizations.  I am including the tables and chi-squared because I think that we can use this as our final analysis file.

@@
 ---
-title: "Draft Visualizationa for Semester Project"
+title: "Draft Visualizations for Semester Project"
 output: word_document
@@
 
+We get a warning that the approximation may be incorrect, likely because some of the values from the table are small.
+Therefore, we cannot draw and conclusions for this test about whether these two variables are related.
+
 ####Visualization of Data
@@
 Based off of the chi-squared test, it is not clear if there is a statistically significant difference in anonymity policies of companies of different sizes.
-However, the fact that the majority of respondents across company sizes do not know their company's anonymity policy is something that has to be addressed, as a study by Milne, et al (1994) has found that participants tended to be more confident in a company's Employee Assistance Program if they felt it was confidential (p.
+However, the fact that the majority of respondents across company sizes do not know their company's anonymity policy is something that has to be addressed in any outreach program, as a study by Milne, et al (1994) has found that participants tended to be more confident in a company's Employee Assistance Program if they felt it was confidential (p.
 141).
@@
 ####Chi-Squared Test
+
+This chi-squared test's p value is very large. Therefore, there is likelt not a relationship between these two variables.
 
@@
 
-Since the p value is less than .01, then we can say that there may be a significant difference in the answers to perceived ease for requesting leave by different company size groups.
-
 ```{r}
@@
 ```
+
+Because the p value is less than .01 we can reject the null and say that we think that there is a relationship between these two variables.
 
@@
 
-Because the p value is not less than .01 we do not reject the null (there are no differences between categories).
-
 ```{r}
@@
 ```
+
+Because the p value is not less than .01 we cannot reject the null. The null variables is that there is no relationship between these two variables.
 
@@
 
-Because the p value is less than .01 we can reject the null and say that we think that there are differences between categories.
-
 ```{r}
@@
 ```
+
+Because the p value is less than .01 we can reject the null and say that we think that there are differences between categories.
 
@@
 MHbG
+prop.table(MHbG, 2)
 ```
@@
 
+The p value is very large.  Therefore, we cannot reject the null hypothesis. The null hypothesis is that these two variables are indepdendent (no relationship between them)
+
+####Create Visualization
+
+```{r}
+t9 <- ggplot(health, aes(x = health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.direct.supervisor.s..))+geom_bar()+facet_grid(~ health$gender) + ggtitle("Comfort with Discussing MH with Supervisor by Gender") + xlab("Would you feel comfortable discussing a mental health disorder with your supervisor?") + ylab("Count")
+t9
+```
+
+####Interpretation of Results
+
+Most respondents across genders indicate that they would be comfortable discussing a mental health disorder with their supervisors.
+With male employees, a lower proportion indicate that they would not be comfortable discussing a mental health disorder with their supervisors.
+Meanwhile, with female and employees of other genders, the results are slightly more evenly split among the three options.
+However, the difference is not statistically significant.
+
 ###Answers by Age Group
@@
 MHbA
+prop.table(MHbA, 2)
 ```
@@
 ```
+
+We get a warning that the approximation may be incorrect, likely because some of the values from the table are small.
+However, it potentially indicates that that the differences between age groups may not be statistically significant (or we do not have enough information).
+
+####Create Visualization
+
+```{r}
+t10 <- ggplot(health, aes(x = health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.direct.supervisor.s..))+geom_bar()+facet_grid(health$AgeGroup ~., scales="free_y") + ggtitle("Comfort with Discussing MH with Supervisor by Age") + xlab("Would you feel comfortable discussing a mental health disorder with your supervisor?") + ylab("Count")
+t10
+```
+
+####Interpretation of Results
+
+Survey respondents in the 17-37 and 37-57 age groups are about evenly split among stating they would feel comfortable discussing a mental health disorder with their supervisor, those who say they would not, and those who say they might.
+In both cases, the majority say they would feel comfortable.
+The next most common response is maybe, and no received the least amount of responses.
+However, in both cases over a quarter of participants in both age groups answered that they would not feel comfortable.
+The 57-77 range has a low number of responses, although in that case "No" is the second most common reponse.
+Given the chi-squared test results and the visualization, it does not appear that age has much of an impact on comfort level in discussing a mental health disorder with a supervisor.
+However, the fact that there are fewer responses from the 37-57 and especially the 57-77 age groups may impact our results.
 
@@
 prop.table(MHCbA, 2)
+```
+
+####Chi-Squared
+
+```{r}
 #Chi-Squared (We get a big chi-quared and a warning it may be incorrect, likely b/c small values for the 57-77 column)
@@
 prop.table(MHCbCS, 2)
+```
+
+####Chi-Squared
+
+```{r}
 #Chi-Squared (the p value is small)

### 2018-11-26 Visualizations/Draft Visualizations Template.Rmd
Updated templates

@@
 #Add labels to tech company org
-TLabel <- factor(health$Is.your.employer.primarily.a.tech.company.organization.,
+health$TLabel <- factor(health$Is.your.employer.primarily.a.tech.company.organization.,
 levels = c(0, 1),
-labels = c("No", "Yes"))
+labels = c("Not primarily tech", "Primarily Tech"))
+```
+
+```{r}
 #Create a crosstab table
-APbT2 <- table(health$Is.your.anonymity.protected.if.you.choose.to.take.advantage.of.mental.health.or.substance.abuse.treatment.resources.provided.by.your.employer., TLabel)
+APbT2 <- table(health$Is.your.anonymity.protected.if.you.choose.to.take.advantage.of.mental.health.or.substance.abuse.treatment.resources.provided.by.your.employer., health$TLabel)
 head(APbT2)
@@
 ```{r}
-#Create Labels for Tech Companies
-techlabel <- c(
-`0` = "Not Primarily a Tech Company",
-`1` = "Primarily a Tech Company")
 #Create Visualization
-t1 <- ggplot(health, aes(x = health$Is.your.anonymity.protected.if.you.choose.to.take.advantage.of.mental.health.or.substance.abuse.treatment.resources.provided.by.your.employer.))+geom_bar()+facet_wrap(health$Is.your.employer.primarily.a.tech.company.organization.
-~ ., labeller = as_labeller(techlabel)) + ggtitle("Anonymity Protections For Tech vs.
+t1 <- ggplot(health, aes(x = health$Is.your.anonymity.protected.if.you.choose.to.take.advantage.of.mental.health.or.substance.abuse.treatment.resources.provided.by.your.employer.))+geom_bar()+facet_wrap(health$TLabel ~ ., scales="free_y") + ggtitle("Anonymity Protections For Tech vs.
 Non-Tech Companies") + xlab("Is your anonymity protected?") + ylab("Count")
@@
 ```{r}
-#Modify Labels
-pd2 <- factor(health$If.a.mental.health.issue.prompted.you.to.request.a.medical.leave.from.work..asking.for.that.leave.would.be.,
+#Modify Labels (ideal if we can get it to fit)
+health$pd2 <- factor(health$If.a.mental.health.issue.prompted.you.to.request.a.medical.leave.from.work..asking.for.that.leave.would.be.,
 levels = c("Very easy", "Somewhat easy", "Neither easy nor difficult","Somewhat difficult", "Very difficult", "I don't know"),
-labels = c("V Easy", "S Easy", "Neutral", "SW Hard", "V Hard", "Don't Know"))
+labels = c("Very easy (VE)", "Somewhat Easy (SE)", "Neutral (N)", "Somewhat Hard (SH)", "Very Hard (VH)", "Don't Know (DK)"))
+#Modify Labels (if health$pd2 does not fit, use this as an alternate)
+health$pd3 <- factor(health$If.a.mental.health.issue.prompted.you.to.request.a.medical.leave.from.work..asking.for.that.leave.would.be.,
+levels = c("Very easy", "Somewhat easy", "Neither easy nor difficult","Somewhat difficult", "Very difficult", "I don't know"),
+labels = c("VE", "SE", "N", "SH", "VH", "DK"))
 ```
@@
 #Crosstab table
-ELDbG <- table(pd2, health$gender)
+ELDbG <- table(health$pd2, health$gender)
 ELDbG
@@
 #Create Visualization
-t2 <- ggplot(health, aes(x = pd2))+geom_bar()+facet_grid(health$gender ~ ., scales="free_y") + ggtitle("Perceived Difficulty of Asking for Leave by Gender") + xlab("Perceived Difficulty Level") + ylab("Count")
+t2 <- ggplot(health, aes(x = health$pd3))+geom_bar()+facet_wrap(health$gender ~ ., scales="free_y") + ggtitle("Perceived Difficulty of Asking for Leave by Gender") + xlab("Perceived Difficulty Level") + ylab("Count")
 t2
 ```
+NOTE:  VE = Very Easy, SE = Somewhat Easy, N = Neutral (or Neither Easy nor Difficult), SH = Somewhat Hard, VH = Very Hard, DK = Don't Know.
 
@@
 #Crosstab table
-ELDbA <- table(pd2, health$AgeGroup)
+ELDbA <- table(health$pd2, health$AgeGroup)
 ELDbA
@@
 #Create Visualization
-t3 <- ggplot(health, aes(x = pd2))+geom_bar()+facet_grid(health$AgeGroup ~ ., scales="free_y") + ggtitle("Perceived Difficulty of Asking for Leave by Age Group") + xlab("Perceived Difficulty Level") + ylab("Count")
+t3 <- ggplot(health, aes(x = health$pd3))+geom_bar()+facet_wrap(health$AgeGroup ~ ., scales="free_y") + ggtitle("Perceived Difficulty of Asking for Leave by Age Group") + xlab("Perceived Difficulty Level") + ylab("Count")
 t3
 ```
+NOTE:  VE = Very Easy, SE = Somewhat Easy, N = Neutral (or Neither Easy nor Difficult), SH = Somewhat Hard, VH = Very Hard, DK = Don't Know.
 
@@
 #Crosstab table
-ELDbCS <- table(pd2, health$CompanySize)
+ELDbCS <- table(health$pd2, health$CompanySize)
 ELDbCS
@@
 ```{r}
-#Modify Labels
-pd3 <- factor(health$If.a.mental.health.issue.prompted.you.to.request.a.medical.leave.from.work..asking.for.that.leave.would.be.,
-levels = c("Very easy", "Somewhat easy", "Neither easy nor difficult","Somewhat difficult", "Very difficult", "I don't know"),
-labels = c("E", "SE", "N", "SH", "H", "D"))
 #Create Visualization
-t4 <- ggplot(health, aes(x = pd3))+geom_bar()+facet_grid(~ health$CompanySize) + ggtitle("Perceived Difficulty of Asking for Leave by Company Size") + xlab("Perceived Difficulty Level") + ylab("Count")
+t4 <- ggplot(health, aes(x = health$pd3))+geom_bar()+facet_wrap(health$CompanySize~ ., scales="free_y") + ggtitle("Perceived Difficulty of Asking for Leave by Company Size") + xlab("Perceived Difficulty Level") + ylab("Count")
 t4
@@
 
-NOTE:  E = Very Easy, S = Somewhat Easy, N = Neutral (or Neither Easy nor Difficult), SH = Somewhat Hard, H = Very Hard, D = Don't Know.
+NOTE:  VE = Very Easy, SE = Somewhat Easy, N = Neutral (or Neither Easy nor Difficult), SH = Somewhat Hard, VH = Very Hard, DK = Don't Know.
 
@@
 ```{r}
-#Modify Labels
+#Modify Labels for mental health benefit provision
 health$mhb2 <- factor(health$Does.your.employer.provide.mental.health.benefits.as.part.of.healthcare.coverage.,
@@
 labels = c("Don't Know", "No", "Ineligible/NA", "Yes"))
+```
+
+```{r}
 #Crosstab Table
-ELDbMHB <- table(pd2, health$mhb2)
+ELDbMHB <- table(health$pd2, health$mhb2)
 ELDbMHB
@@
 ```{r}
-t5 <- ggplot(health, aes(x = pd3))+geom_bar()+facet_grid(~ health$mhb2, scales="free_y") + ggtitle("Perceived Difficulty of Asking for Leave by MH Benefit Provision") + xlab("Perceived Difficulty Level") + ylab("Count")
+t5 <- ggplot(health, aes(x = health$pd3))+geom_bar()+facet_wrap(~ health$mhb2, scales="free_y") + ggtitle("Perceived Difficulty of Asking for Leave by MH Benefit Provision") + xlab("Perceived Difficulty Level") + ylab("Count")
 t5
 ```
-NOTE:  E = Very Easy, S = Somewhat Easy, N = Neutral (or Neither Easy nor Difficult), SH = Somewhat Hard, H = Very Hard, D = Don't Know.
+NOTE:  VE = Very Easy, SE = Somewhat Easy, N = Neutral (or Neither Easy nor Difficult), SH = Somewhat Hard, VH = Very Hard, DK = Don't Know.
+
+####Interpretation of Results
+
+For those who do not get mental health benefits, more participants responded that they perceive it as somewhat difficult to request leave for a mental health issue than any other response (with somewhat easy being the second most common).
+Among those who do get mental health benefits, most indicated they perceive it as very easy or somwhat easy to request leave for a mental health issue.
+Most of those who did not know if mental health benefits are offered inidicated they perceived it to be somewhat easy to request leave for a mental health issue.
+Those who are ineligible (or for whom it was not applicable) were evently split among the responses, although relatively few people selected this response compared to the others.
+However, the difference between the two variables does not appear to be statistically significant.
 
@@
 ```{r}
-ELDbEDM <- table(pd2, health$Has.your.employer.ever.formally.discussed.mental.health..for.example..as.part.of.a.wellness.campaign.or.other.official.communication..)
+ELDbEDM <- table(health$pd2, health$Has.your.employer.ever.formally.discussed.mental.health..for.example..as.part.of.a.wellness.campaign.or.other.official.communication..)
 ELDbEDM
@@
 ```{r}
-t6 <- ggplot(health, aes(x = pd2))+geom_bar()+facet_grid( health$Has.your.employer.ever.formally.discussed.mental.health..for.example..as.part.of.a.wellness.campaign.or.other.official.communication..
+t6 <- ggplot(health, aes(x = health$pd3))+geom_bar()+facet_wrap( health$Has.your.employer.ever.formally.discussed.mental.health..for.example..as.part.of.a.wellness.campaign.or.other.official.communication..
 ~., scales="free_y") + ggtitle("Perceived Difficulty of Asking for Leave by MH Discussion by Employer") + xlab("Perceived Difficulty Level") + ylab("Count")
@@
 ```
+NOTE:  VE = Very Easy, SE = Somewhat Easy, N = Neutral (or Neither Easy nor Difficult), SH = Somewhat Hard, VH = Very Hard, DK = Don't Know.
 
@@
 ```{r}
-ELDbEOR <- table(pd2, health$Does.your.employer.offer.resources.to.learn.more.about.mental.health.concerns.and.options.for.seeking.help.)
+ELDbEOR <- table(health$pd2, health$Does.your.employer.offer.resources.to.learn.more.about.mental.health.concerns.and.options.for.seeking.help.)
 ELDbEOR
@@
 ```{r}
-t7 <- ggplot(health, aes(x = pd2))+geom_bar()+facet_grid( health$Does.your.employer.offer.resources.to.learn.more.about.mental.health.concerns.and.options.for.seeking.help.
+t7 <- ggplot(health, aes(x = health$pd3))+geom_bar()+facet_wrap( health$Does.your.employer.offer.resources.to.learn.more.about.mental.health.concerns.and.options.for.seeking.help.
 ~., scales="free_y") + ggtitle("Perceived Difficulty of Asking for Leave by Mental Health Resource Provision") + xlab("Perceived Difficulty Level") + ylab("Count")
@@
 ```{r}
-ELDbPR <- table(pd2, health$Have.you.observed.or.experienced.an.unsupportive.or.badly.handled.response.to.a.mental.health.issue.in.your.current.or.previous.workplace.)
+ELDbPR <- table(health$pd2, health$Have.you.observed.or.experienced.an.unsupportive.or.badly.handled.response.to.a.mental.health.issue.in.your.current.or.previous.workplace.)
 ELDbPR
@@
 ```{r}
-#Modify Labels
+#Modify Labels for unsupportive response to make them shorter
 health$epr <- factor(health$Have.you.observed.or.experienced.an.unsupportive.or.badly.handled.response.to.a.mental.health.issue.in.your.current.or.previous.workplace.,
@@
 labels = c("Don't Know", "N/A", "No", "Yes, experienced", "Yes, observed"))
-table(pd2, health$epr)
+table(health$pd2, health$epr)
 ```
@@
 ```{r}
-t8 <- ggplot(health, aes(x = pd3))+geom_bar()+facet_grid(~ health$epr) + ggtitle("Perceived Difficulty of Asking for Leave by Exp.
+t8 <- ggplot(health, aes(x = health$pd3))+geom_bar()+facet_wrap(health$epr ~., scales="free_y") + ggtitle("Perceived Difficulty of Asking for Leave by Exp.
 with Poor MH Response") + xlab("Perceived Difficulty Level") + ylab("Count")
@@
 ```{r}
-t10 <- ggplot(health, aes(x = health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.direct.supervisor.s..))+geom_bar()+facet_grid(health$AgeGroup ~., scales="free_y") + ggtitle("Comfort with Discussing MH with Supervisor by Age") + xlab("Would you feel comfortable discussing a mental health disorder with your supervisor?") + ylab("Count")
+t10 <- ggplot(health, aes(x = health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.direct.supervisor.s..))+geom_bar()+facet_wrap(health$AgeGroup ~., scales="free_y") + ggtitle("Comfort with Discussing MH with Supervisor by Age") + xlab("Would you feel comfortable discussing a mental health disorder with your supervisor?") + ylab("Count")
 t10

### 2018-11-27 Visualizations/Draft Visualizations Template.Rmd
Update Draft Visualizations Template.Rmd

@@
 
-This chi-squared test's p value is very large. Therefore, there is likelt not a relationship between these two variables.
-
 ```{r}
@@
 ```
+
+This chi-squared test's p value is very large. Therefore, there is likely not a relationship between these two variables.
 
@@
 ```
-
 NOTE:  VE = Very Easy, SE = Somewhat Easy, N = Neutral (or Neither Easy nor Difficult), SH = Somewhat Hard, VH = Very Hard, DK = Don't Know.
@@
 
-Because the p value is not less than .01 we cannot reject the null. The null variables is that there is no relationship between these two variables.
+Because the p value is not less than .01 we cannot reject the null. The null hypothesis is that there is no relationship between these two variables.
 
@@
 
-Survey respondents in the 17-37 and 37-57 age groups are about evenly split among stating they would feel comfortable discussing a mental health disorder with their supervisor, those who say they would not, and those who say they might.
-In both cases, the majority say they would feel comfortable.
-The next most common response is maybe, and no received the least amount of responses.
+The majority of respondents in the 17-37 and 37-57 age groups responded that they would feel comfortable discussing a mental health disorder with their supervisor.
+The next most common response is that they might, and no received the least amount of responses from the 17-37 and 37-57 age groups.
 However, in both cases over a quarter of participants in both age groups answered that they would not feel comfortable.
@@
 ###Answers by Company Size
+
 ```{r}
@@
 MHbCS
+prop.table(MHbCS, 2)
 ```
@@
 
+Because the p value is not less than .01 we cannot reject the null. The null hypothesis is that there is no relationship between these two variables.
+
+####Create Visualization
+
+```{r}
+t11 <- ggplot(health, aes(x = health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.direct.supervisor.s..))+geom_bar()+facet_wrap(health$CompanySize ~., scales="free_y") + ggtitle("Comfort with Discussing MH with Supervisor by Company Size") + xlab("Would you feel comfortable discussing a mental health disorder with your supervisor?") + ylab("Count")
+t11
+```
+
+####Interpretation of Results
+
+The pattern that we see in the data visualization is interesting.
+For companies in the 26-100, 100-500, and 500-1000 groups (and to a lesser extent in the 6-25 group), fewer respondents indicate they would not feel comfortable discussing a mental health disorder with their supervisor than selecting the "Maybe" or "Yes" options.
+However, in the "More than 1000" group, most respondents indicated they would not feel comfortable (although a significant amount answered "Maybe" or "Yes").
+It is possible that for larger companies people may feel less comfortable discussing these issues with supervisors because it the organization is more bureaucratic or there are employee/supervisor relationships that are less personal.
+However, it is also possible that these results indicate that the results are depedendent on the company as well as other factors.
+Because the null is larger than .01, we fail to reject the null that there is a significant relationship between the two variables.
+
 ###Answers by If They Ever Saw A Poor Response to Mental Health Issue
@@
 ```{r}
-MHbPR <- table(health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.direct.supervisor.s.., health$Have.you.observed.or.experienced.an.unsupportive.or.badly.handled.response.to.a.mental.health.issue.in.your.current.or.previous.workplace.)
+MHbPR <- table(health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.direct.supervisor.s.., health$Do.you.think.that.discussing.a.mental.health.disorder.with.your.employer.would.have.negative.consequences.)
 MHbPR
+prop.table(MHbPR, 2)
 ```
@@
 
-###Answers by If They Think Supervisor Would View Them Negatively If They Knew You Suffered From a Mental Health Issue
+###Answers by If They Think Discussing a Mental Health Disorder with Employer Would Have Negative Consequences
 
 ```{r}
+MHbVN <- table(health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.direct.supervisor.s.., health$Do.you.think.that.discussing.a.mental.health.disorder.with.your.employer.would.have.negative.consequences.)
+MHbVN
+```
 
+####Chi-Squared
+
+```{r}
+chisq.test(MHbVN)
 ```
+
+Because the p value is less than .01 we can reject the null and say that we think that there is a statistically significant relationship between these two categories.
+
+####Create Visualization
+
+```{r}
+#Modify Labels for perception of mental health disclosure impact
+health$negimp <- factor(health$Do.you.think.that.discussing.a.mental.health.disorder.with.your.employer.would.have.negative.consequences.,
+levels = c("Maybe", "No", "Yes"),
+labels = c("Maybe Expect a Negative Impact", "Do Not Expect Negative Impact", "Expect Negative Impact"))
+#Check Results
+table(health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.direct.supervisor.s.., health$negimp)
+```
+
+```{r}
+t12 <- ggplot(health, aes(x = health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.direct.supervisor.s..))+geom_bar()+facet_wrap(health$negimp ~., scales="free_y") + ggtitle("Comfort with Discussing MH with Supervisor by Perception of Negative Impact") + xlab("Would you feel comfortable discussing a mental health disorder with your supervisor?") + ylab("Count")
+t12
+```
+
+####Interpret Results
+
+The results here are fairly clear.
+Most people who responded that they feel that discussing a mental health disorder would have a negative impact also are not comfortable discussing a mental health issue with a supervisor.
+The reverse is also true, most people who responded that they do not feel that discussing a mental health disorder would have a negative impact also indicate that they would be comfortable discussing a mental health issue with their supervisor.
+For those who responded that there maybe a negative impact, most also answered that they may be comfortable discussing a mental health disorder with their supervisor (with "no" being the second most common response for that group).
+Therefore, any outreach that we do or program that we plan needs to keep this in mind.
 
@@
 MHCbG
+prop.table(MHCbG, 2)
 ```
@@
 ```
+
+The chi-squared is very large.  Therefore, we cannot reject the null hypothesis that these categories are independent.
+
+####Create Visualization
+
+```{r}
+t13 <- ggplot(health, aes(x = health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.coworkers.))+geom_bar()+facet_wrap(health$gender ~., scales="free_y") + ggtitle("Comfort with Discussing MH with Coworkers by Gender") + xlab("Would you feel comfortable discussing a mental health disorder with your coworkers?") + ylab("Count")
+t13
+```
+
+####Interpret Results
+
+The chi-squared test appears to indicate that there is not a significant relationship between gender and comfort with discussing mental health with coworkers.
+However, these results may be impacted by the fact that there are fewer respondents who are female or another gender than men.
+However, a higher proportion of female respondents indicate that they do not feel comfortable discussing a mental health disorder with coworkers.
+However, across all genders the most common response is "maybe."  This indicates that a lot may depend on their relationships with individual coworkers (e.g., they may feel comfortable with discussing with a specific coworker).
+Interestingly, as stated above, most respondents across genders indicated that they would be comfortable discussing a mental health disorder with their supervisors.
 
@@
 ```
+
+We get a warning that the approximation may be incorrect, likely because some of the values from the table are small.
+However, it potentially indicates that that the differences between age groups is not statistically significant.
+
+####Create Visualization
+
+```{r}
+t14 <- ggplot(health, aes(x = health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.coworkers.))+geom_bar()+facet_wrap(health$AgeGroup ~., scales="free_y") + ggtitle("Comfort with Discussing MH with Coworkers by Age Group") + xlab("Would you feel comfortable discussing a mental health disorder with your coworkers?") + ylab("Count")
+t14
+```
+
+####Interpret Results
+
+Members of the 17-37 and 37-57 age group have a similar pattern.
+The majority of respondents indicated that they might feel comfortable discussing a mental health disorder with coworkers, with the second most common response being that they would not.
+When I looked at the comfort level of discussing a mental health disorder with supervisors, the results were different.
+Interestingly, as stated above, the majority of respondents in the 17-37 and 37-57 age groups responded that they would feel comfortable discussing a mental health disorder with their supervisor.
+Therefore, there may be a higher comfort level discussing mental health disorders with supervisors than other coworkers (or respondents' comfort level may vary by the coworker).
 
@@
 
+The chi-squared is less than .01.  Therefore, we can reject the null and say that there is a relationship between these two variables.
+
+####Creating the Visualization
+
+```{r}
+t17 <- ggplot(health, aes(x = health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.coworkers.))+geom_bar()+facet_wrap(health$Do.you.think.that.team.members.co.workers.would.view.you.more.negatively.if.they.knew.you.suffered.from.a.mental.health.issue.
+~., scales="free_y") + ggtitle("Comfort with Discussing MH with Coworkers by Perceived Negative Impact") + xlab("Would you feel comfortable discussing a mental health disorder with your coworkers?") + ylab("Count")
+t17
+```
+
+####Interpretation of Results
+
+In this visualization we see that perceived impact of discussing a mental health disorder with coworkers has a potentially significant impact on comfort level with discussing a mental health disorder with coworkers.
+For those who feel that they would be viewed negatively by coworkers if they knew the respondent had a mental health issue, they frequently answer that they would not feel comfortable discussing a mental health disorder with coworkers.
+For those who feel like they are negatively viewed by coworkers because of a mental health issue, appear to be evenly split between maybe being comfortable and not being comfortable.
+Meanwhile, for those who feel that they are not viewed more negatively because of a mental health disorder, they most frequently say they would be comfortable discussing mental health with coworkers.
+For those who did not think they would be viewed negatively, they most frequently select that they may be comfortable discussing a mental health disorder with other coworkers, with yes being the second most common response from that group.
+This indicates that we may want to consider providing training to employees about mental illness in the workplace.
+
 #Works Cited

### 2018-11-28 Visualizations/Draft Visualizations Template.Rmd
Complete my section of visualizations

@@
 ```{r}
-MHbPR <- table(health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.direct.supervisor.s.., health$Do.you.think.that.discussing.a.mental.health.disorder.with.your.employer.would.have.negative.consequences.)
+MHbPR <- table(health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.direct.supervisor.s.., health$Have.you.observed.or.experienced.an.unsupportive.or.badly.handled.response.to.a.mental.health.issue.in.your.current.or.previous.workplace.)
 MHbPR
@@
 ```
+
+####Create Visualization
+
+```{r}
+t17 <- ggplot(health, aes(x = health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.direct.supervisor.s..))+geom_bar()+facet_wrap(health$Have.you.observed.or.experienced.an.unsupportive.or.badly.handled.response.to.a.mental.health.issue.in.your.current.or.previous.workplace.
+~., scales="free_y") + ggtitle("Comfort with Discussing MH w/ Supervisor by Exp.
+w/ Poor Workplace Response") + xlab("Would you feel comfortable discussing a mental health disorder with your supervisor?") + ylab("Count")
+t17
+```
+
+####Interpret Results
+
+When asked about experience with a poorly handled response to mental health, respondents who were not sure if they expereinced it were evenly split between answering that they maybe comfortable discussing a mental health disorder with supervisors or not comfortable (there was also a large group that said they would be comfortable).
+For those who answered that they did not have experience with a poor response, they also answered yes more often than maybe and no when also asked about their comfort with discussing a mental health disorder with a supervisor.
+Interestingly, those who stated "Yes, I observed" a poor response to mental health in the workplace were evenly split selected maybe the most often when also asked if they would feel comfortable discussing a mental health disorder with coworkers (and "yes" was the second most common response).
+However, those who stated that they experienced a poorly handled response were evenly split between the yes, no, and maybe answers when asked about comfort level discussing mental health with a supervisor.
 
@@
 ```{r}
-#Chi-Squared (We get a big chi-quared and a warning it may be incorrect, likely b/c small values for the 57-77 column)
 chisq.test(MHCbA)
@@
 
+The chi-squared test shows a p value that is less than 0.01.
+Therefore, we can reject the null hypothesis (that there is no relationship between these variables).
+This indicates that there may be a relationship between company size and comfort level with talking to coworkers about a mental health issue.
+
+####Create Visualization
+
+```{r}
+t15 <- ggplot(health, aes(x = health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.coworkers.))+geom_bar()+facet_wrap(health$CompanySize ~., scales="free_y") + ggtitle("Comfort with Discussing MH with Coworkers by Company Size") + xlab("Would you feel comfortable discussing a mental health disorder with your coworkers?") + ylab("Count")
+t15
+```
+
+####Interpret Results
+
+Respondents from companies with 1-5 employees are roughly evenly split among the three responses (yes, no, maybe) when asked if they would feel comfortable discussing a mental health disorder with coworkers.
+Results are similar with companies for 6-25 employees, but a lower proportion of employees in that category indicate they would be comfortable.
+For the 26-100 and 100-500 employee companies, most indicate that they may be comfortable with "no" being the second most common response.
+Respondents from companies with 500-1000 employees also select maybe the most often, but "yes" is the second most common response.
+Finally, respondents from companies with more than 1000 employees select the "no" answer the most often, with maybe being the second most common.
+The results indicate that there may be a relationship between company size and willingness to talk to coworkers about mental illness.
+However, the variation in responses also indicates that the reasons for the comfort, discomfort, or uncertainty may vary by company.
+
 ###Answers by If They Ever Saw A Poor Response to Mental Health Issue
@@
 ```
+
+The chi-squared test shows a p value that is less than 0.01.
+Therefore, we can reject the null hypothesis (that there is no relationship between these variables).
+This indicates that there may be a relationship between experience with a poor response to a mental health issue with talking to coworkers about a mental health issue.
+
+####Create Visualization
+
+```{r}
+t16 <- ggplot(health, aes(x = health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.coworkers.))+geom_bar()+facet_wrap(health$Have.you.observed.or.experienced.an.unsupportive.or.badly.handled.response.to.a.mental.health.issue.in.your.current.or.previous.workplace.
+~., scales="free_y") + ggtitle("Comfort Discussing MH w/ Coworkers by Exp.
+w/ Poor Workplace MH Response") + xlab("Would you feel comfortable discussing a mental health disorder with your coworkers?") + ylab("Count")
+t16
+```
+
+####Interpret Results
+
+When asked about experience with a poorly handled response to mental health, respondents across all categories except for "N/A" (which had relatively few respondents), also answered that they maybe comfortable discussing a mental health disorder with coworkers.
+Interestingly, those who stated "Yes, I observed" a poor response to mental health in the workplace were evenly split between the maybe and no answers when also asked if they would feel comfortable discussing a mental health disorder with coworkers.
+However, those who stated that they experienced a poorly handled response selected "Maybe" most often when also asked if they would feel comfortable discussing a mental health disorder with coworkers.
+The remainder were about evenly split between the "no" and "yes" answers.
+This may indicate that observing a poorly handled response to a mental health issue in the workplace may have a greater negative effect on willingness to discuss with coworkers than those experiencing it.
 

### 2018-11-28 Visualizations/Draft Visualizations Template.Rmd
visualization code
Visualization code for age group, gender and physical vs mental health

@@
 library(ggplot2)
+library(grid)
+library(gridExtra)
 health <- read.csv("mentalsurvey_clean.csv")
@@
 
-```{r setup, include=FALSE}
+###Distribution of Mental health disorders
+```{r}
+
+#since some people have multiple disorders, we have to split them 
+tmp = health %>% separate(mhd, 
+                          sep = '\\|',
+                          c('mhd_1', 'mhd_2', 'mhd_3', 'mhd_4', 'mhd_5',
+                            'mhd_6', 'mhd_7', 'mhd_8', 'mhd_9'),
+                          fill = 'right')
+
+chk = tmp %>% select(matches('mhd_[1-9]'))
+
+comb = as.vector(t(chk))
+comb1 = comb[comb != ""&!is.na(comb)]
+
+#Shortening the factor levels by splitting
+disorders=sapply(strsplit(comb1, split = " \\("), `[`, 1)
+dataf <- as.data.frame(matrix(disorders))
+colnames(dataf)<- "Disorder"
+#Removing inconsistent response
+subdataf <- subset(dataf, disorders != "I haven\'t been formally diagnosed, so I felt uncomfortable answering, but Social Anxiety and Depression.")
+count_disorder <-data.frame(count(subdataf, Disorder, sort = TRUE))
+count_disorder
+```
+
+```{r}
+
+reorder_size <- function(x) {
+  factor(x, levels = names(sort(table(x), decreasing = TRUE)))
+}
+#Plot to see the distribution of current mental health illness
+p <- ggplot(data=subdataf, aes(x = reorder_size(Disorder)))+
+  geom_bar(fill='dark blue')+
+  theme(axis.text.x = element_text(angle = 90, hjust = 1))
+
+p+xlab("Current Mental health disorders")+ggtitle("Distribution of Mental health disorders currently")
+```
+
+####Interpretation of Results
+
+The most common mental health disorder appears to be mood disorder with a count of 325, followed by anxiety disorder with a count of 272.
+
+###Distribution of mental health status among gender
+
+```{r}
+gender_disorder <- table(health$Do.you.currently.have.a.mental.health.disorder., health$gender)
+gender_disorder
+```
+```{r}
+#Table: % of who may, don't or have mental disorder among genders
+rowprop <- prop.table(gender_disorder,1) 
+rowprop
+```
+
+```{r}
+dr1 <-as.data.frame(rowprop)
+# Distribution of respondents among gender provided they may/have/donot have a mental diorder 
+ggplot(data = dr1, aes(x =Var1 , y = Freq, fill = Var2)) + 
+  geom_bar(stat = 'identity', position = 'dodge', alpha = 2/3) +              
+  labs(x = NULL, y = 'Proportion', fill = 'Gender')+ggtitle('Distribution of mental health status among genders (1)')
+```
+
+####Interpretation of results
+
+The table and figure above shows that among the people that said Yes, 32.3% are females, 63.4% are males and 4.2% are otherss.
+Among the people that said No, 81.4% are males, 18.3% are females and 0.2% are others.Among the people that said Maybe, 79.5% are males, 17.3% are females and 3.1% are others.
+
+```{r}
+#Table : % of each level gender who may, don't or have mental disorder
+colprop <- prop.table(gender_disorder,2)
+colprop
+```
+```{r}
+# Distribution of respondents who may/have/donot have a mental diorder over the gender
+dr2 <-as.data.frame(colprop)
+ggplot(data = dr2, aes(x =Var2 , y = Freq, fill = Var1)) + 
+  geom_bar(stat = 'identity', position = 'dodge', alpha = 2/3) +              
+  labs(x = NULL, y = 'Proportion', fill = 'Disorder')+ggtitle('Distribution of mental health status among genders (2)')
+```
+
+####Interpretation of results
+
+The table and figure above show that the proportion of females who said Yes (0.53) are more than the proportion of females that said no (0.29) amd maybe (0.16).
+The proportion of males that said No (0.42) are more than the proportion of males who said Yes (0.33) and Maybe (0.23).
+In the gender Other, the proportion that said Yes (0.67) are more than the proportion that said No (0.03) and Maybe (0.28).
+
+###
+```{r}
+summary(health$age)
+```
+```{r}
+#Creating lavbels for age groups
+labs <- c(paste(seq(17, 74, by = 20), seq(37, 80, by = 20),
+                sep = "-"))
+health$AgeGroup <- cut(health$age, breaks = c(seq(17, 74, by = 20), Inf), labels = labs, right = FALSE)
+
+agegr <- table(health$Do.you.currently.have.a.mental.health.disorder.,health$AgeGroup)
+ageprop <- prop.table(agegr,2)
+ageprop
+```
+```{r}
+dfageprop <- as.data.frame(ageprop)
+
+#Distribution of respondents reporting a mental disorder by age groups
+ggplot(data = dfageprop, aes(x =Var2 , y = Freq, fill = Var1)) + 
+  geom_bar(stat = 'identity', position = 'dodge', alpha = 2/3) +              
+  labs(x = "Age Groups", y = 'Proportion', fill = 'Disorder')
+```
+
+####Interpretation of results
+
+The table and plot above show that in the age group of 17-37, 40% said they currently have a mental disorder, 38% said they donot have a mental disorder currently and 21.9% said are not sure.
+In the 37-57 age group, 39.4% said they donot have a mental disorder currently, 37.3% said Yes and 23.2% said maybe or are not sure.
+In the 57-77 agegroup, 50% said Yes, 41.6% said No and 8.3% said maybe.
+```{r}
+ageprop1 <- prop.table(agegr,1)
+ageprop1
+```
+
+```{r}
+dfageprop1 <- as.data.frame(ageprop1)
+ggplot(data = dfageprop1, aes(x =Var1 , y = Freq, fill = Var2)) + 
+  geom_bar(stat = 'identity', position = 'dodge', alpha = 2/3) +              
+  labs(x = "Disorder", y = 'Proportion', fill = 'Age group')
+```
+
+####Interepretion of results
+
+The table and plot above show that among the people that said they have mental disorder currently, 71.6% lie in the 17-37 age group, 27% lie in the 37-57 age group and 1.3% lie in the age group of 57-77.
+Among the people that said No, 69.6% lie in the 17-37 age group, 29.2% lie in the 37-57 age group and 1.1% lie in the 57-77 group.
+Among the people that said Maybe, 69.6% liein the 17-37 age group, 29.9% lie in the 37-57 age group and .3% lie in the 57-77 age group.
+
+###Potential Negative Consequences for Discussing Health Issues with Employer: Physical vs. Mental
+```{r}
 knitr::opts_chunk$set(echo = TRUE)
+#Creating a table with gender and mental health responses
+tab <- table(health$Do.you.think.that.discussing.a.mental.health.disorder.with.your.employer.would.have.negative.consequences., health$gender)
+tab
 ```
+```{r}
+#Creating a table with gender and physical health responses
+tab1 <- table(health$Do.you.think.that.discussing.a.physical.health.issue.with.your.employer.would.have.negative.consequences., health$gender)
+tab1
+```
+```{r}
+#creating the combined plot
+tabdf <- as.data.frame(tab)
+tab1df <- as.data.frame(tab1)
+
+plot1 <- ggplot(data = tabdf, aes(x = Var1, y =Freq, fill = Var2)) + 
+  geom_bar(stat = 'identity', position = 'dodge', alpha = 2/3) +              
+  labs(x = "Mental health disorders", y = 'count')+ theme(legend.position='none')
+
+plot2 <- ggplot(data = tab1df, aes(x = Var1, y =Freq, fill = Var2)) + 
+  geom_bar(stat = 'identity', position = 'dodge', alpha = 2/3) +              
+  labs(x = "Physical health disorders", y = 'count', fill = 'Gender')
+title1=textGrob("Negative consequences: Mental vs Physial", gp=gpar(fontface="bold"))
+grid.arrange(plot1, plot2,ncol=2,top = title1, widths = c(3/4,1))
+```
+
+####Interpretation of Results
+
+The figure above shows that majority of people are certain that discussing physical health issues with their employers will not result in negative consequences.
+Very few believe that discussing physical health issues will have negative consequences.
+The responses to whether discussing mental health disorders with employers will result in negative consequences is more divided.
+Some people believe that discussing mental health disorders will have a negative consequence.
+This is probably due to the stigma at workplace which may make them believe that they might face negative consequences if their mental issues are brought infront of a employer.
+However, there are still more people who believe there won't be any negative consequences.
+This could be because they have already developed a smooth employer-employee relationship.
+There are comparatively more number of people who are unsure of whether or not there would be any negative consequences if mental health disorders are discussed with their employers.
 
@@
 (1994).
-Factors Influencing Employees’ Propensity to Use an Employee Assistance Program.
-Personnel Psychology, 47(1), 123–145.
+Factors Influencing Employees???
+Propensity to Use an Employee Assistance Program.
+Personnel Psychology, 47(1), 123???145.
 Retrieved October 24, 2018 from http://search.ebscohost.com.proxy-um.researchport.umd.edu/login.aspx?direct=true&db=bth&AN=9411113184&site=ehost-live

### 2018-11-28 Visualizations/disorder_visualization.R
updated code

@@ -135,6 +135,29 @@ ggplot(data = dfageprop1, aes(x =Var1 , y = Freq, fill = Var2)) +
   geom_bar(stat = 'identity', position = 'dodge', alpha = 2/3) +              
   labs(x = "Disorder", y = 'Proportion', fill = 'Age group')
 
+# NEGATIVE CONSEQUENCES ON DISUCSSING HEALTH ISSUES: MENTAL VS PHYSICAL
+
+#Creating a table with gender and mental health responses
+tab <- table(health$Do.you.think.that.discussing.a.mental.health.disorder.with.your.employer.would.have.negative.consequences., health$gender)
+tab
+#Creating a table with gender and physical health responses
+tab1 <- table(health$Do.you.think.that.discussing.a.physical.health.issue.with.your.employer.would.have.negative.consequences., health$gender)
+tab1
+
+#creating the combined plot
+tabdf <- as.data.frame(tab)
+tab1df <- as.data.frame(tab1)
+
+plot1 <- ggplot(data = tabdf, aes(x = Var1, y =Freq, fill = Var2)) + 
+  geom_bar(stat = 'identity', position = 'dodge', alpha = 2/3) +              
+  labs(x = "Mental health disorders", y = 'count')+ theme(legend.position='none')
+
+plot2 <- ggplot(data = tab1df, aes(x = Var1, y =Freq, fill = Var2)) + 
+  geom_bar(stat = 'identity', position = 'dodge', alpha = 2/3) +              
+  labs(x = "Physical health disorders", y = 'count', fill = 'Gender')
+title1=textGrob("Negative consequences: Mental vs Physial", gp=gpar(fontface="bold"))
+grid.arrange(plot1, plot2,ncol=2,top = title1, widths = c(3/4,1))
+
 #POSSIBLE FACTORS IN WHETHER EMPLOYEE FEELS ASKING FOR LEAVE WOULD BE DIFFICULT
 
 #Answers by Gender (crosstab table)

### 2018-11-29 Visualizations/Draft Visualizations Template.Rmd
Updated  Rmd

@@
 
-#Section 1: Showing that Mental and Behavioral Health Issues Impact Workers
+#Section 1: Distribution of mental health disorders based on different demographics
 
 ###Distribution of Mental health disorders
+
 ```{r}
@@
 
-###
+###Distribution of mental health disorder based on age groups
+
 ```{r}
@@
 ```{r}
-#Creating lavbels for age groups
+#Creating labels for age groups
 labs <- c(paste(seq(17, 74, by = 20), seq(37, 80, by = 20),
@@
 
-###Potential Negative Consequences for Discussing Health Issues with Employer: Physical vs. Mental
+#Section 2: What are Other Companies Doing to Assist workers with Mental and Behavioral Health Policies
+
+```{r}
+
+```
+
+#Section 3: What are Factors that Might Limit the Impact of Behavioral Health Outreach
+
+###Potential Negative Consequences for discussing Health Issues with Employer: Physical vs. Mental
+
+If employees feel that discussing physical or mental health issues would have negative consequences. If so, they may be less likely to reach out for help.
+
 ```{r}
@@
 This is probably due to the stigma at workplace which may make them believe that they might face negative consequences if their mental issues are brought infront of a employer.
+This will make them less likely to reach out for help, discuss their issues with their employers, take time off work.
 However, there are still more people who believe there won't be any negative consequences.
@@
 There are comparatively more number of people who are unsure of whether or not there would be any negative consequences if mental health disorders are discussed with their employers.
-
-#Section 2: What are Other Companies Doing to Assist workers with Mental and Behavioral Health Policies
-
-```{r}
-
-```
-
-#Section 3: What are Factors that Might Limit the Impact of Behavioral Health Outreach
 

### 2018-11-29 Visualizations/disorder_visualization.R

@@ -119,6 +119,7 @@ labs <- c(paste(seq(17, 74, by = 20), seq(37, 80, by = 20),
 labs
 health$AgeGroup <- cut(health$age, breaks = c(seq(17, 74, by = 20), Inf), labels = labs, right = FALSE)
 View(health$AgeGroup)
+write.csv(health, "output.csv")
 
 agegr <- table(health$Do.you.currently.have.a.mental.health.disorder.,health$AgeGroup)
 ageprop <- prop.table(agegr,2)

### 2018-11-29 Visualizations/Draft Visualizations Template.Rmd
Update Files

@@
 ---
-title: "Draft Visualizations for Semester Project"
+title: "Analysis File and R Plots"
 output: word_document
@@
 t7 <- ggplot(health, aes(x = health$pd3))+geom_bar()+facet_wrap( health$Does.your.employer.offer.resources.to.learn.more.about.mental.health.concerns.and.options.for.seeking.help.
-~., scales="free_y") + ggtitle("Perceived Difficulty of Asking for Leave by Mental Health Resource Provision") + xlab("Perceived Difficulty Level") + ylab("Count")
+~., scales="free_y") + ggtitle("Perceived Difficulty of Asking for Leave by MH Resource Provision") + xlab("Perceived Difficulty Level") + ylab("Count")
 t7
@@
 ```{r}
-t12 <- ggplot(health, aes(x = health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.direct.supervisor.s..))+geom_bar()+facet_wrap(health$negimp ~., scales="free_y") + ggtitle("Comfort with Discussing MH with Supervisor by Perception of Negative Impact") + xlab("Would you feel comfortable discussing a mental health disorder with your supervisor?") + ylab("Count")
+t12 <- ggplot(health, aes(x = health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.direct.supervisor.s..))+geom_bar()+facet_wrap(health$negimp ~., scales="free_y") + ggtitle("Comfort with Discussing MH with Supervisor by Perceived Negative Impact") + xlab("Would you feel comfortable discussing a mental health disorder with your supervisor?") + ylab("Count")
 t12
@@
 ```{r}
-t13 <- ggplot(health, aes(x = health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.coworkers.))+geom_bar()+facet_wrap(health$gender ~., scales="free_y") + ggtitle("Comfort with Discussing MH with Coworkers by Gender") + xlab("Would you feel comfortable discussing a mental health disorder with your coworkers?") + ylab("Count")
+t13 <- ggplot(health, aes(x = health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.coworkers.))+geom_bar()+facet_wrap(health$gender ~., scales="free_y") + ggtitle("Comfort with Discussing MH with Coworkers by Gender") + xlab("Would you feel comfortable discussing a MH disorder with your coworkers?") + ylab("Count")
 t13
@@
 t16 <- ggplot(health, aes(x = health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.coworkers.))+geom_bar()+facet_wrap(health$Have.you.observed.or.experienced.an.unsupportive.or.badly.handled.response.to.a.mental.health.issue.in.your.current.or.previous.workplace.
-~., scales="free_y") + ggtitle("Comfort Discussing MH w/ Coworkers by Exp.
+~., scales="free_y") + ggtitle("Comfort Discuss MH w/ Coworkers by Exp.
 w/ Poor Workplace MH Response") + xlab("Would you feel comfortable discussing a mental health disorder with your coworkers?") + ylab("Count")
@@
 t17 <- ggplot(health, aes(x = health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.coworkers.))+geom_bar()+facet_wrap(health$Do.you.think.that.team.members.co.workers.would.view.you.more.negatively.if.they.knew.you.suffered.from.a.mental.health.issue.
-~., scales="free_y") + ggtitle("Comfort with Discussing MH with Coworkers by Perceived Negative Impact") + xlab("Would you feel comfortable discussing a mental health disorder with your coworkers?") + ylab("Count")
+~., scales="free_y") + ggtitle("Comfort Discussing MH with Coworkers by Perceived Negative Impact") + xlab("Would you feel comfortable discussing a mental health disorder with your coworkers?") + ylab("Count")
 t17

### 2018-11-30 Visualizations/Draft Visualizations Template.Rmd
Updated rcode
Monalisa_Rcode

--- 2018-11-29 Visualizations/Draft Visualizations Template.Rmd
@@
 
+```
+###Analzing the relationship between perceiving the negative impact of mental illness at previous workplace and the impact at current workplace
+
+####Plotting the ggplot for the independent variable "Do you think that discussing a mental health disorder with previous employers would have negative consequences?"
+
+```{r}
+ggplot(health, aes(x = health$Do.you.think.that.discussing.a.mental.health.disorder.with.previous.employers.would.have.negative.consequences.)) + geom_bar() + ggtitle("Discussing mental health disorder with previous employer resulting in negative consequences") + xlab("Response") + ylab("Count")
+summary(health$Do.you.think.that.discussing.a.mental.health.disorder.with.previous.employers.would.have.negative.consequences.)
+
+```
+
+####Interpreting the results
+From the above ggplot, we can observe that a majority of respondents(615) feel that discussing mental health disorders with some of their previous employers resulted in negative consequences for them.
+While a significant number of respondents responded that they do not know, we can conclude from the graph that the majority did experience negative consequences after discussing mental health disorders with their previous employers
+
+###Plotting the ggplot for the dependent variable "Do you think that discussing a mental health disorder with your employer would have negative consequences?"
+
+```{r}
+ggplot(health, aes(x = health$Do.you.think.that.discussing.a.mental.health.disorder.with.your.employer.would.have.negative.consequences.)) + geom_bar() + ggtitle("Discussing mental health disorder with current employer resulting in negative consequences") + xlab("Response") + ylab("Count")
+summary(health$Do.you.think.that.discussing.a.mental.health.disorder.with.your.employer.would.have.negative.consequences.)
+
+```
+
+####Interpretation of results
+From the above ggplot, we can see that a vast majority of respondents(487) are not sure if discussing mental health disorders with their current employers would have negative consequences; followed by about 438 respondents who do not think that it could lead to negative consequences
+
+####Chi-squared test
+```{r}
+t1<-table(health$Do.you.think.that.discussing.a.mental.health.disorder.with.previous.employers.would.have.negative.consequences., health$Do.you.think.that.discussing.a.mental.health.disorder.with.your.employer.would.have.negative.consequences.)
+chisq.test(t1)
+```
+
+####Interpret results
+We can see that the p-value of the Chi-squared test is very small, meaning we can reject the hypothesis of independence.
+Thus there is a relationship between perceiving the negative impact of mental illness at previous workplace and the impact at current workplace
+
 #Works Cited

### 2018-11-30 Visualizations/Draft Visualizations Template.Rmd
Changes for pretty display
pretty display without ##

@@
 #Loading the Data and Necessary Packages
-```{r}
+```{r, message=FALSE, warning=FALSE, include=FALSE}
+knitr::opts_chunk$set(comment = NA)
 library(dplyr)
@@
 library(gridExtra)
+library(knitr)
 health <- read.csv("mentalsurvey_clean.csv")
@@
 count_disorder <-data.frame(count(subdataf, Disorder, sort = TRUE))
-count_disorder
+kable(count_disorder)
 ```
@@
   geom_bar(stat = 'identity', position = 'dodge', alpha = 2/3) +              
-  labs(x = "Age Groups", y = 'Proportion', fill = 'Disorder')
+  labs(x = "Age Groups", y = 'Proportion', fill = 'Disorder')+ggtitle('Distribution of mental health status based on age groups (1)')
 ```
@@
   geom_bar(stat = 'identity', position = 'dodge', alpha = 2/3) +              
-  labs(x = "Disorder", y = 'Proportion', fill = 'Age group')
+  labs(x = "Disorder", y = 'Proportion', fill = 'Age group')+ggtitle('Distribution of mental health status based on age groups (2)')
 ```
@@
 
-```
 ###Analzing the relationship between perceiving the negative impact of mental illness at previous workplace and the impact at current workplace

### 2018-11-30 Visualizations/Draft Visualizations Template.Rmd
Changes in the package loading
Removed package loading messages

@@
 #Loading the Data and Necessary Packages
-```{r, message=FALSE, warning=FALSE, include=FALSE}
+```{r, message=FALSE, warning=FALSE}
 knitr::opts_chunk$set(comment = NA)

### 2018-11-30 Visualizations/Draft Visualizations Template.Rmd
latest changes

@@
 
-#Section 2: What are Other Companies Doing to Assist workers with Mental and Behavioral Health Policies
-
-```{r}
+#Section 2: Analysis of distribution of mental health benefits offered by companies in the dataset
+
+###Distribution of employers offering mental healh benefits as part of healthcare coverage
+
+```{r}
+#Creating a table for the variable "Does your employer provide mental health benefits as part of healthcare coverage?""
+
+table(health$Does.your.employer.provide.mental.health.benefits.as.part.of.healthcare.coverage.)
+
+barplot(table(health$Does.your.employer.provide.mental.health.benefits.as.part.of.healthcare.coverage.))
+
+```
+
+####Interpretation of results
+
+From the above output, we can see that out of a total 1433 companies, only 531 provide mental health benefits as part of healthcare coverage, which is approximately one-third of the responses.
+
+###Distribution of employers offering resources to learn more about mental health concerns and options for seeking help
+
+```{r}
+table(health$Does.your.employer.offer.resources.to.learn.more.about.mental.health.concerns.and.options.for.seeking.help.)
+
+barplot(table(health$Does.your.employer.offer.resources.to.learn.more.about.mental.health.concerns.and.options.for.seeking.help.))
+```
+
+####Interpretation of results
+
+From the above output, we can see that a very small number of companies from the dataset of 1433 entries offer resources to employees to learn more about mental health concerns and options for seeking help.i.e., only 295 employers.
+For the dataset under study, this implies that a very small number of employers are taking steps to aquaint their employees with mental health benefits in the respective companies.
+Also, we can see that a significant number of employees, i.e., 320 out of 1433, do not know if their employers offer resporces to seek help regading mental health concerns.
+This also implies lack of initiative in generating awareness about mental health-related policies.
+
+###Do Companies in the survey dataset have formal discussions to Assist workers with Mental and Behavioral Health Policies
+
+For companies with mental health care options available, let us find out what percentage have a formal discussion (as part of a campaign/official communication) with employees to generate awareness about the mental health care policies.
+Here, we can create subset for companies with mental health care options available.
+This dataset(subset) will contain only those companies that provide mental health benefits as part of healthcare coverage
+
+```{r}
+Company<-subset(health, Does.your.employer.provide.mental.health.benefits.as.part.of.healthcare.coverage.=="Yes")
+Company
+```
+
+###Percentage of employers who have a formal discussion about mental health with their employees
+
+```{r}
+#Creating a table for for the variable related to employers formally discussing mental health with employees
+table(Company$Has.your.employer.ever.formally.discussed.mental.health..for.example..as.part.of.a.wellness.campaign.or.other.official.communication..)
+#Computing the percentage
+percent<-table(Company$Has.your.employer.ever.formally.discussed.mental.health..for.example..as.part.of.a.wellness.campaign.or.other.official.communication..)/length(Company$Has.your.employer.ever.formally.discussed.mental.health..for.example..as.part.of.a.wellness.campaign.or.other.official.communication..)
+#The parameter percent gives us the value of the percenntage needed
+percent
+```
+
+####Interpretation of results
+
+The value of the parameter percent in the above output for the column "Yes" gives us the percentage of employers who have formally discussed mental health with their employees (considering only those companies who provide mental health benefits to their employees).
+Thus, about 26.5 percent of employers hve a formal discussion about mental health and related policies with their employees.
+For the dataset under study, this is a very small number.
+In order to make the employees familiar with the mental health policies and benefits, it is crucial that the employers have a formal discussion with them.
+
+####Visualizing the proportion of responses for employers formally discussing mental health with theri employees
+
+```{r}
+Company<-droplevels(Company)
+barplot(table(Company$Has.your.employer.ever.formally.discussed.mental.health..for.example..as.part.of.a.wellness.campaign.or.other.official.communication..), xlab = "Responses", ylab = "Count", main = "Do Employers Formally Discuss Mental Health?")
 
@@
 
+###Analzing the relationship between perceiving the negative impact of mental illness at previous workplace and the impact at current workplace
+
+It is likely that if employees perceived a negative impact from discussing mental illness at a previous workplace, they may have similar perception at the current workplace as well. 
+We can plot the ggplot for the independent variable "Do you think that discussing a mental health disorder with previous employers would have negative consequences?"
+
+```{r}
+ggplot(health, aes(x = health$Do.you.think.that.discussing.a.mental.health.disorder.with.previous.employers.would.have.negative.consequences.)) + geom_bar() + ggtitle("Discussing mental health disorder with previous employer resulting in negative consequences") + xlab("Response") + ylab("Count")
+summary(health$Do.you.think.that.discussing.a.mental.health.disorder.with.previous.employers.would.have.negative.consequences.)
+```
+
+From the above ggplot, we can observe that a majority of respondents(615) feel that discussing mental health disorders with some of their previous employers resulted in negative consequences for them.
+While a significant number of respondents responded that they do not know, we can conclude from the graph that the majority did experience negative consequences after discussing mental health disorders with their previous employers
+
+Plotting the ggplot for the dependent variable "Do you think that discussing a mental health disorder with your employer would have negative consequences?"
+
+```{r}
+ggplot(health, aes(x = health$Do.you.think.that.discussing.a.mental.health.disorder.with.your.employer.would.have.negative.consequences.)) + geom_bar() + ggtitle("Discussing mental health disorder with current employer resulting in negative consequences") + xlab("Response") + ylab("Count")
+summary(health$Do.you.think.that.discussing.a.mental.health.disorder.with.your.employer.would.have.negative.consequences.)
+```
+
+From the above ggplot, we can see that a vast majority of respondents(487) are not sure if discussing mental health disorders with their current employers would have negative consequences; followed by about 438 respondents who do not think that it could lead to negative consequences.
+
+####Chi-squared test
+
+```{r}
+m1<-table(health$Do.you.think.that.discussing.a.mental.health.disorder.with.previous.employers.would.have.negative.consequences., health$Do.you.think.that.discussing.a.mental.health.disorder.with.your.employer.would.have.negative.consequences.)
+chisq.test(m1)
+```
+
+####Interpretation of results
+
+We can see from the above chi-squared test that the p-value is very small, meaning we can reject the hypothesis of independence.
+Thus there is a relationship between perceiving the negative impact of mental illness at previous workplace and perceiving the same at the current workplace.
+Employees who have perceived or experienced a negative impact of discussing a mental illness with their previous employer feel the same way about discussing it with their current employer.
+This type of attitude may be the result of some form of negative impact such as bias, discrimination or lack of oppurtunities that they faced at the previous workplace.
+This might have influenced their decision to discusstheir mental illnesses with their current employer as well.
+
 ##Anonymity Policies
@@
 Thus there is a relationship between perceiving the negative impact of mental illness at previous workplace and the impact at current workplace
+
+###Analzing the relationship between perceiving the negative impact of mental illness at previous workplace and the impact at current workplace
+
+####Plotting the ggplot for the independent variable "Do you think that discussing a mental health disorder with previous employers would have negative consequences?"
+
+```{r}
+ggplot(health, aes(x = health$Do.you.think.that.discussing.a.mental.health.disorder.with.previous.employers.would.have.negative.consequences.)) + geom_bar() + ggtitle("Discussing mental health disorder with previous employer resulting in negative consequences") + xlab("Response") + ylab("Count")
+summary(health$Do.you.think.that.discussing.a.mental.health.disorder.with.previous.employers.would.have.negative.consequences.)
+```
 

### 2018-12-01 Visualizations/Draft Visualizations Template.Rmd
Final change
Commit

@@
 
+###Distribution of mental health disorder based on geography
+
+```{r}
+table(health$What.US.state.or.territory.do.you.live.in. , health$Do.you.currently.have.a.mental.health.disorder.)
+```
+
+####Interpretation of results
+
+From the above table output, we can see that the US state with the majority of mental health illness cases is California, followed by Illoinois and New York
+
 #Section 2: Analysis of distribution of mental health benefits offered by companies in the dataset
@@
 
-###Percentage of employers who have a formal discussion about mental health with their employees
+####Percentage of employers who have a formal discussion about mental health with their employees
 

### 2018-12-01 Visualizations/Draft Visualizations Template.Rmd
latest
Changed font size added labels to charts where it was missing

@@
 title: "Draft Visualizations for Semester Project"
-output: word_document
+output:
+  word_document: default
 ---
@@
 
-barplot(table(health$Does.your.employer.provide.mental.health.benefits.as.part.of.healthcare.coverage.))
+barplot(table(health$Does.your.employer.provide.mental.health.benefits.as.part.of.healthcare.coverage.), xlab = "Responses", ylab = "Count", main = "Do Employers Offer Mental Health Benefits?")
 
@@
 
-barplot(table(health$Does.your.employer.offer.resources.to.learn.more.about.mental.health.concerns.and.options.for.seeking.help.))
+barplot(table(health$Does.your.employer.offer.resources.to.learn.more.about.mental.health.concerns.and.options.for.seeking.help.), xlab = "Responses", ylab = "Count", main = "Do Employers Offer Resources Related to Mental Health?")
 ```
@@
 Company<-subset(health, Does.your.employer.provide.mental.health.benefits.as.part.of.healthcare.coverage.=="Yes")
-Company
+
 ```
@@
 ```{r}
-ggplot(health, aes(x = health$Do.you.think.that.discussing.a.mental.health.disorder.with.previous.employers.would.have.negative.consequences.)) + geom_bar() + ggtitle("Discussing mental health disorder with previous employer resulting in negative consequences") + xlab("Response") + ylab("Count")
+ggplot(health, aes(x = health$Do.you.think.that.discussing.a.mental.health.disorder.with.previous.employers.would.have.negative.consequences.)) + geom_bar() + ggtitle("Discussing mental health disorder with previous employer resulting in negative consequences") + xlab("Response") + ylab("Count") + theme(axis.title=element_text(size=12))
 summary(health$Do.you.think.that.discussing.a.mental.health.disorder.with.previous.employers.would.have.negative.consequences.)
@@
 ```{r}
-ggplot(health, aes(x = health$Do.you.think.that.discussing.a.mental.health.disorder.with.your.employer.would.have.negative.consequences.)) + geom_bar() + ggtitle("Discussing mental health disorder with current employer resulting in negative consequences") + xlab("Response") + ylab("Count")
+ggplot(health, aes(x = health$Do.you.think.that.discussing.a.mental.health.disorder.with.your.employer.would.have.negative.consequences.)) + geom_bar() + ggtitle("Discussing mental health disorder with current employer resulting in negative consequences") + xlab("Response") + ylab("Count") + theme(axis.title=element_text(size=12))
 summary(health$Do.you.think.that.discussing.a.mental.health.disorder.with.your.employer.would.have.negative.consequences.)
@@
 ```{r}
-t0 <- ggplot(health, aes(x = health$Is.your.anonymity.protected.if.you.choose.to.take.advantage.of.mental.health.or.substance.abuse.treatment.resources.provided.by.your.employer.))+geom_bar()+facet_wrap(~health$CompanySize, scales="free_y") + ggtitle("Perceived Difficulty of Asking for Leave by Gender") + xlab("Perceived Difficulty Level") + ylab("Count")
+t0 <- ggplot(health, aes(x = health$Is.your.anonymity.protected.if.you.choose.to.take.advantage.of.mental.health.or.substance.abuse.treatment.resources.provided.by.your.employer.))+geom_bar()+facet_wrap(~health$CompanySize, scales="free_y") + ggtitle("Perceived Difficulty of Asking for Leave by Gender") + xlab("Perceived Difficulty Level") + ylab("Count")+ theme(axis.title=element_text(size=12))
 t0
@@
 t1 <- ggplot(health, aes(x = health$Is.your.anonymity.protected.if.you.choose.to.take.advantage.of.mental.health.or.substance.abuse.treatment.resources.provided.by.your.employer.))+geom_bar()+facet_wrap(health$TLabel ~ ., scales="free_y") + ggtitle("Anonymity Protections For Tech vs.
-Non-Tech Companies") + xlab("Is your anonymity protected?") + ylab("Count")
+Non-Tech Companies") + xlab("Is your anonymity protected?") + ylab("Count") + theme(axis.title=element_text(size=12))
 t1
@@
 #Create Visualization
-t2 <- ggplot(health, aes(x = health$pd3))+geom_bar()+facet_wrap(health$gender ~ ., scales="free_y") + ggtitle("Perceived Difficulty of Asking for Leave by Gender") + xlab("Perceived Difficulty Level") + ylab("Count")
+t2 <- ggplot(health, aes(x = health$pd3))+geom_bar()+facet_wrap(health$gender ~ ., scales="free_y") + ggtitle("Perceived Difficulty of Asking for Leave by Gender") + xlab("Perceived Difficulty Level") + ylab("Count") + theme(axis.title=element_text(size=12))
 t2
@@
 #Create Visualization
-t3 <- ggplot(health, aes(x = health$pd3))+geom_bar()+facet_wrap(health$AgeGroup ~ ., scales="free_y") + ggtitle("Perceived Difficulty of Asking for Leave by Age Group") + xlab("Perceived Difficulty Level") + ylab("Count")
+t3 <- ggplot(health, aes(x = health$pd3))+geom_bar()+facet_wrap(health$AgeGroup ~ ., scales="free_y") + ggtitle("Perceived Difficulty of Asking for Leave by Age Group") + xlab("Perceived Difficulty Level") + ylab("Count") + theme(axis.title=element_text(size=12))
 t3
@@
 ```{r}
-t5 <- ggplot(health, aes(x = health$pd3))+geom_bar()+facet_wrap(~ health$mhb2, scales="free_y") + ggtitle("Perceived Difficulty of Asking for Leave by MH Benefit Provision") + xlab("Perceived Difficulty Level") + ylab("Count")
+t5 <- ggplot(health, aes(x = health$pd3))+geom_bar()+facet_wrap(~ health$mhb2, scales="free_y") + ggtitle("Perceived Difficulty of Asking for Leave by Mental Health Benefit Provision") + xlab("Perceived Difficulty Level") + ylab("Count") + theme(axis.title=element_text(size=12))
 t5
@@
 t6 <- ggplot(health, aes(x = health$pd3))+geom_bar()+facet_wrap( health$Has.your.employer.ever.formally.discussed.mental.health..for.example..as.part.of.a.wellness.campaign.or.other.official.communication..
-~., scales="free_y") + ggtitle("Perceived Difficulty of Asking for Leave by MH Discussion by Employer") + xlab("Perceived Difficulty Level") + ylab("Count")
+~., scales="free_y") + ggtitle("Perceived Difficulty of Asking for Leave by Mental Health Disc.
+by Employer") + xlab("Perceived Difficulty Level") + ylab("Count") + theme(axis.title=element_text(size=12))
 t6
@@
 t7 <- ggplot(health, aes(x = health$pd3))+geom_bar()+facet_wrap( health$Does.your.employer.offer.resources.to.learn.more.about.mental.health.concerns.and.options.for.seeking.help.
-~., scales="free_y") + ggtitle("Perceived Difficulty of Asking for Leave by Mental Health Resource Provision") + xlab("Perceived Difficulty Level") + ylab("Count")
+~., scales="free_y") + ggtitle("Perceived Difficulty of Asking for Leave by Mental Health Resource Provision") + xlab("Perceived Difficulty Level") + ylab("Count") + theme(axis.title=element_text(size=12))
 t7
@@
 t8 <- ggplot(health, aes(x = health$pd3))+geom_bar()+facet_wrap(health$epr ~., scales="free_y") + ggtitle("Perceived Difficulty of Asking for Leave by Exp.
-with Poor MH Response") + xlab("Perceived Difficulty Level") + ylab("Count")
+with Poor MH Response") + xlab("Perceived Difficulty Level") + ylab("Count") + theme(axis.title=element_text(size=12))
 t8
@@
 ```{r}
-t9 <- ggplot(health, aes(x = health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.direct.supervisor.s..))+geom_bar()+facet_grid(~ health$gender) + ggtitle("Comfort with Discussing MH with Supervisor by Gender") + xlab("Would you feel comfortable discussing a mental health disorder with your supervisor?") + ylab("Count")
+t9 <- ggplot(health, aes(x = health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.direct.supervisor.s..))+geom_bar()+facet_grid(~ health$gender) + ggtitle("Comfort with Discussing Mental Health Disorder with Supervisor by Gender") + xlab("Would you feel comfortable discussing a mental health disorder with your supervisor?") + ylab("Count") + theme(axis.title=element_text(size=12), axis.text=element_text(size=10))
 t9
@@
 ```{r}
-t10 <- ggplot(health, aes(x = health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.direct.supervisor.s..))+geom_bar()+facet_wrap(health$AgeGroup ~., scales="free_y") + ggtitle("Comfort with Discussing MH with Supervisor by Age") + xlab("Would you feel comfortable discussing a mental health disorder with your supervisor?") + ylab("Count")
+t10 <- ggplot(health, aes(x = health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.direct.supervisor.s..))+geom_bar()+facet_wrap(health$AgeGroup ~., scales="free_y") + ggtitle("Comfort with Discussing Mental Health Disorder with Supervisor by Age") + xlab("Would you feel comfortable discussing a mental health disorder with your supervisor?") + ylab("Count") + theme(axis.title=element_text(size=12), axis.text=element_text(size=10))
 t10
@@
 ```{r}
-t11 <- ggplot(health, aes(x = health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.direct.supervisor.s..))+geom_bar()+facet_wrap(health$CompanySize ~., scales="free_y") + ggtitle("Comfort with Discussing MH with Supervisor by Company Size") + xlab("Would you feel comfortable discussing a mental health disorder with your supervisor?") + ylab("Count")
+t11 <- ggplot(health, aes(x = health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.direct.supervisor.s..))+geom_bar()+facet_wrap(health$CompanySize ~., scales="free_y") + ggtitle("Comfort with Disc.
+Mental Health Disorder with Supervisor by Company Size") + xlab("Would you feel comfortable discussing a mental health disorder with your supervisor?") + ylab("Count") + theme(axis.title=element_text(size=12), axis.text=element_text(size=10))
 t11
@@
 t17 <- ggplot(health, aes(x = health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.direct.supervisor.s..))+geom_bar()+facet_wrap(health$Have.you.observed.or.experienced.an.unsupportive.or.badly.handled.response.to.a.mental.health.issue.in.your.current.or.previous.workplace.
-~., scales="free_y") + ggtitle("Comfort with Discussing MH w/ Supervisor by Exp.
-w/ Poor Workplace Response") + xlab("Would you feel comfortable discussing a mental health disorder with your supervisor?") + ylab("Count")
+~., scales="free_y") + ggtitle("Comfort with Disc.
+MH w/ Supervisor by Exp.
+w/ Poor Workplace Response") + xlab("Would you feel comfortable discussing a mental health disorder with your supervisor?") + ylab("Count") + theme(axis.title=element_text(size=12), axis.text=element_text(size=10))
 t17
@@
 ```{r}
-t12 <- ggplot(health, aes(x = health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.direct.supervisor.s..))+geom_bar()+facet_wrap(health$negimp ~., scales="free_y") + ggtitle("Comfort with Discussing MH with Supervisor by Perception of Negative Impact") + xlab("Would you feel comfortable discussing a mental health disorder with your supervisor?") + ylab("Count")
+t12 <- ggplot(health, aes(x = health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.direct.supervisor.s..))+geom_bar()+facet_wrap(health$negimp ~., scales="free_y") + ggtitle("Comfort w/ Disc.
+MH with Supervisor by Perception of Negative Impact") + xlab("Would you feel comfortable discussing a mental health disorder with your supervisor?") + ylab("Count") + theme(axis.title=element_text(size=12), axis.text=element_text(size=10))
 t12
@@
 ```{r}
-t13 <- ggplot(health, aes(x = health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.coworkers.))+geom_bar()+facet_wrap(health$gender ~., scales="free_y") + ggtitle("Comfort with Discussing MH with Coworkers by Gender") + xlab("Would you feel comfortable discussing a mental health disorder with your coworkers?") + ylab("Count")
+t13 <- ggplot(health, aes(x = health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.coworkers.))+geom_bar()+facet_wrap(health$gender ~., scales="free_y") + ggtitle("Comfort with Discussing MH Disorder with Coworkers by Gender") + xlab("Would you feel comfortable discussing a mental health disorder with your coworkers?") + ylab("Count") + theme(axis.title=element_text(size=12), axis.text=element_text(size=10))
 t13
@@
 ```{r}
-t14 <- ggplot(health, aes(x = health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.coworkers.))+geom_bar()+facet_wrap(health$AgeGroup ~., scales="free_y") + ggtitle("Comfort with Discussing MH with Coworkers by Age Group") + xlab("Would you feel comfortable discussing a mental health disorder with your coworkers?") + ylab("Count")
+t14 <- ggplot(health, aes(x = health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.coworkers.))+geom_bar()+facet_wrap(health$AgeGroup ~., scales="free_y") + ggtitle("Comfort with Discussing MH Disorder with Coworkers by Age Group") + xlab("Would you feel comfortable discussing a mental health disorder with your coworkers?") + ylab("Count") + theme(axis.title=element_text(size=12), axis.text=element_text(size=10))
 t14
@@
 ```{r}
-t15 <- ggplot(health, aes(x = health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.coworkers.))+geom_bar()+facet_wrap(health$CompanySize ~., scales="free_y") + ggtitle("Comfort with Discussing MH with Coworkers by Company Size") + xlab("Would you feel comfortable discussing a mental health disorder with your coworkers?") + ylab("Count")
+t15 <- ggplot(health, aes(x = health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.coworkers.))+geom_bar()+facet_wrap(health$CompanySize ~., scales="free_y") + ggtitle("Comfort with Discussing MH Disorder with Coworkers by Company Size") + xlab("Would you feel comfortable discussing a mental health disorder with your coworkers?") + ylab("Count") + theme(axis.title=element_text(size=12), axis.text=element_text(size=10))
 t15
@@
 t16 <- ggplot(health, aes(x = health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.coworkers.))+geom_bar()+facet_wrap(health$Have.you.observed.or.experienced.an.unsupportive.or.badly.handled.response.to.a.mental.health.issue.in.your.current.or.previous.workplace.
-~., scales="free_y") + ggtitle("Comfort Discussing MH w/ Coworkers by Exp.
-w/ Poor Workplace MH Response") + xlab("Would you feel comfortable discussing a mental health disorder with your coworkers?") + ylab("Count")
+~., scales="free_y") + ggtitle("Comfort Disc.
+MH w/ Coworkers by Exp.
+w/ Poor Workplace MH Response") + xlab("Would you feel comfortable discussing a mental health disorder with your coworkers?") + ylab("Count") + theme(axis.title=element_text(size=12), axis.text=element_text(size=10))
 t16
@@
 t17 <- ggplot(health, aes(x = health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.coworkers.))+geom_bar()+facet_wrap(health$Do.you.think.that.team.members.co.workers.would.view.you.more.negatively.if.they.knew.you.suffered.from.a.mental.health.issue.
-~., scales="free_y") + ggtitle("Comfort with Discussing MH with Coworkers by Perceived Negative Impact") + xlab("Would you feel comfortable discussing a mental health disorder with your coworkers?") + ylab("Count")
+~., scales="free_y") + ggtitle("Comfort w/ Disc.
+MH Disorder with Coworkers by Perceived Negative Impact") + xlab("Would you feel comfortable discussing a mental health disorder with your coworkers?") + ylab("Count") + theme(axis.title=element_text(size=12), axis.text=element_text(size=10))
 t17

### 2018-12-01 Visualizations/Draft Visualizations Template.Rmd
final titles fit

@@
 
-barplot(table(health$Does.your.employer.offer.resources.to.learn.more.about.mental.health.concerns.and.options.for.seeking.help.), xlab = "Responses", ylab = "Count", main = "Do Employers Offer Resources Related to Mental Health?")
+barplot(table(health$Does.your.employer.offer.resources.to.learn.more.about.mental.health.concerns.and.options.for.seeking.help.), xlab = "Responses", ylab = "Count", main = "Do Employers Offer Resources\nRelated to Mental Health?")
 ```
@@
 ```{r}
-ggplot(health, aes(x = health$Do.you.think.that.discussing.a.mental.health.disorder.with.previous.employers.would.have.negative.consequences.)) + geom_bar() + ggtitle("Discussing mental health disorder with previous employer resulting in negative consequences") + xlab("Response") + ylab("Count") + theme(axis.title=element_text(size=12))
+ggplot(health, aes(x = health$Do.you.think.that.discussing.a.mental.health.disorder.with.previous.employers.would.have.negative.consequences.)) + geom_bar() + ggtitle("Discussing mental health disorder with previous\nemployer resulting in negative consequences") + xlab("Response") + ylab("Count") + theme(axis.title=element_text(size=12))
 summary(health$Do.you.think.that.discussing.a.mental.health.disorder.with.previous.employers.would.have.negative.consequences.)
@@
 ```{r}
-ggplot(health, aes(x = health$Do.you.think.that.discussing.a.mental.health.disorder.with.your.employer.would.have.negative.consequences.)) + geom_bar() + ggtitle("Discussing mental health disorder with current employer resulting in negative consequences") + xlab("Response") + ylab("Count") + theme(axis.title=element_text(size=12))
+ggplot(health, aes(x = health$Do.you.think.that.discussing.a.mental.health.disorder.with.your.employer.would.have.negative.consequences.)) + geom_bar() + ggtitle("Discussing mental health disorder with\ncurrent employer resulting in negative consequences") + xlab("Response") + ylab("Count") + theme(axis.title=element_text(size=12))
 summary(health$Do.you.think.that.discussing.a.mental.health.disorder.with.your.employer.would.have.negative.consequences.)
@@
 #Create Visualization
-t1 <- ggplot(health, aes(x = health$Is.your.anonymity.protected.if.you.choose.to.take.advantage.of.mental.health.or.substance.abuse.treatment.resources.provided.by.your.employer.))+geom_bar()+facet_wrap(health$TLabel ~ ., scales="free_y") + ggtitle("Anonymity Protections For Tech vs.
-Non-Tech Companies") + xlab("Is your anonymity protected?") + ylab("Count") + theme(axis.title=element_text(size=12))
+t1 <- ggplot(health, aes(x = health$Is.your.anonymity.protected.if.you.choose.to.take.advantage.of.mental.health.or.substance.abuse.treatment.resources.provided.by.your.employer.))+geom_bar()+facet_wrap(health$TLabel ~ ., scales="free_y") + ggtitle("Anonymity Protections for Tech\nvs.Non-Tech Companies") + xlab("Is your anonymity protected?") + ylab("Count") + theme(axis.title=element_text(size=12))
 t1
@@
 #Create Visualization
-t4 <- ggplot(health, aes(x = health$pd3))+geom_bar()+facet_wrap(health$CompanySize~ ., scales="free_y") + ggtitle("Perceived Difficulty of Asking for Leave by Company Size") + xlab("Perceived Difficulty Level") + ylab("Count")
+t4 <- ggplot(health, aes(x = health$pd3))+geom_bar()+facet_wrap(health$CompanySize~ ., scales="free_y") + ggtitle("Perceived Difficulty of Asking for Leave\nby Company Size") + xlab("Perceived Difficulty Level") + ylab("Count")
 t4
@@
 ```{r}
-t5 <- ggplot(health, aes(x = health$pd3))+geom_bar()+facet_wrap(~ health$mhb2, scales="free_y") + ggtitle("Perceived Difficulty of Asking for Leave by Mental Health Benefit Provision") + xlab("Perceived Difficulty Level") + ylab("Count") + theme(axis.title=element_text(size=12))
+t5 <- ggplot(health, aes(x = health$pd3))+geom_bar()+facet_wrap(~ health$mhb2, scales="free_y") + ggtitle("Perceived Difficulty of Asking for Leave by Mental\nHealth Benefit Provision") + xlab("Perceived Difficulty Level") + ylab("Count") + theme(axis.title=element_text(size=12))
 t5
@@
 t6 <- ggplot(health, aes(x = health$pd3))+geom_bar()+facet_wrap( health$Has.your.employer.ever.formally.discussed.mental.health..for.example..as.part.of.a.wellness.campaign.or.other.official.communication..
-~., scales="free_y") + ggtitle("Perceived Difficulty of Asking for Leave by Mental Health Disc.
-by Employer") + xlab("Perceived Difficulty Level") + ylab("Count") + theme(axis.title=element_text(size=12))
+~., scales="free_y") + ggtitle("Perceived Difficulty of Asking for Leave by Mental Health\nDiscussion by Employer") + xlab("Perceived Difficulty Level") + ylab("Count") + theme(axis.title=element_text(size=12))
 t6
@@
 t7 <- ggplot(health, aes(x = health$pd3))+geom_bar()+facet_wrap( health$Does.your.employer.offer.resources.to.learn.more.about.mental.health.concerns.and.options.for.seeking.help.
-~., scales="free_y") + ggtitle("Perceived Difficulty of Asking for Leave by Mental Health Resource Provision") + xlab("Perceived Difficulty Level") + ylab("Count") + theme(axis.title=element_text(size=12))
+~., scales="free_y") + ggtitle("Perceived Difficulty of Asking for Leave by Mental\nHealth Resource Provision") + xlab("Perceived Difficulty Level") + ylab("Count") + theme(axis.title=element_text(size=12))
 t7
@@
 ```{r}
-t8 <- ggplot(health, aes(x = health$pd3))+geom_bar()+facet_wrap(health$epr ~., scales="free_y") + ggtitle("Perceived Difficulty of Asking for Leave by Exp.
-with Poor MH Response") + xlab("Perceived Difficulty Level") + ylab("Count") + theme(axis.title=element_text(size=12))
+t8 <- ggplot(health, aes(x = health$pd3))+geom_bar()+facet_wrap(health$epr ~., scales="free_y") + ggtitle("Perceived Difficulty of Asking for Leave by Experience\nwith Poor Mental health Response") + xlab("Perceived Difficulty Level") + ylab("Count") + theme(axis.title=element_text(size=12))
 t8
@@
 ```{r}
-t9 <- ggplot(health, aes(x = health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.direct.supervisor.s..))+geom_bar()+facet_grid(~ health$gender) + ggtitle("Comfort with Discussing Mental Health Disorder with Supervisor by Gender") + xlab("Would you feel comfortable discussing a mental health disorder with your supervisor?") + ylab("Count") + theme(axis.title=element_text(size=12), axis.text=element_text(size=10))
+t9 <- ggplot(health, aes(x = health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.direct.supervisor.s..))+geom_bar()+facet_grid(~ health$gender) + ggtitle("Comfort with Discussing Mental Health\nDisorder with Supervisor by Gender") + xlab("Would you feel comfortable discussing a mental health\ndisorder with your supervisor?") + ylab("Count") + theme(axis.title=element_text(size=12), axis.text=element_text(size=10))
 t9
@@
 ```{r}
-t10 <- ggplot(health, aes(x = health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.direct.supervisor.s..))+geom_bar()+facet_wrap(health$AgeGroup ~., scales="free_y") + ggtitle("Comfort with Discussing Mental Health Disorder with Supervisor by Age") + xlab("Would you feel comfortable discussing a mental health disorder with your supervisor?") + ylab("Count") + theme(axis.title=element_text(size=12), axis.text=element_text(size=10))
+t10 <- ggplot(health, aes(x = health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.direct.supervisor.s..))+geom_bar()+facet_wrap(health$AgeGroup ~., scales="free_y") + ggtitle("Comfort with Discussing Mental Health\n Disorder with Supervisor by Age") + xlab("Would you feel comfortable discussing a mental health\ndisorder with your supervisor?") + ylab("Count") + theme(axis.title=element_text(size=12), axis.text=element_text(size=10))
 t10
@@
 ```{r}
-t11 <- ggplot(health, aes(x = health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.direct.supervisor.s..))+geom_bar()+facet_wrap(health$CompanySize ~., scales="free_y") + ggtitle("Comfort with Disc.
-Mental Health Disorder with Supervisor by Company Size") + xlab("Would you feel comfortable discussing a mental health disorder with your supervisor?") + ylab("Count") + theme(axis.title=element_text(size=12), axis.text=element_text(size=10))
+t11 <- ggplot(health, aes(x = health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.direct.supervisor.s..))+geom_bar()+facet_wrap(health$CompanySize ~., scales="free_y") + ggtitle("Comfort with Discussion of Mental Health\nDisorder with Supervisor by Company Size") + xlab("Would you feel comfortable discussing a mental health\ndisorder with your supervisor?") + ylab("Count") + theme(axis.title=element_text(size=12), axis.text=element_text(size=10))
 t11
@@
 t17 <- ggplot(health, aes(x = health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.direct.supervisor.s..))+geom_bar()+facet_wrap(health$Have.you.observed.or.experienced.an.unsupportive.or.badly.handled.response.to.a.mental.health.issue.in.your.current.or.previous.workplace.
-~., scales="free_y") + ggtitle("Comfort with Disc.
-MH w/ Supervisor by Exp.
-w/ Poor Workplace Response") + xlab("Would you feel comfortable discussing a mental health disorder with your supervisor?") + ylab("Count") + theme(axis.title=element_text(size=12), axis.text=element_text(size=10))
+~., scales="free_y") + ggtitle("Comfort with Discussing Mental Health with\nSupervisor by Experience with Poor Workplace Response") + xlab("Would you feel comfortable discussing a mental health\ndisorder with your supervisor?") + ylab("Count") + theme(axis.title=element_text(size=12), axis.text=element_text(size=10))
 t17
@@
 ```{r}
-t12 <- ggplot(health, aes(x = health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.direct.supervisor.s..))+geom_bar()+facet_wrap(health$negimp ~., scales="free_y") + ggtitle("Comfort w/ Disc.
-MH with Supervisor by Perception of Negative Impact") + xlab("Would you feel comfortable discussing a mental health disorder with your supervisor?") + ylab("Count") + theme(axis.title=element_text(size=12), axis.text=element_text(size=10))
+t12 <- ggplot(health, aes(x = health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.direct.supervisor.s..))+geom_bar()+facet_wrap(health$negimp ~., scales="free_y") + ggtitle("Comfort with Discussing Mental Health disorder\nwith Supervisor by Perception of Negative Impact") + xlab("Would you feel comfortable discussing a mental health disorder\nwith your supervisor?") + ylab("Count") + theme(axis.title=element_text(size=12), axis.text=element_text(size=10))
 t12
@@
 ```{r}
-t13 <- ggplot(health, aes(x = health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.coworkers.))+geom_bar()+facet_wrap(health$gender ~., scales="free_y") + ggtitle("Comfort with Discussing MH Disorder with Coworkers by Gender") + xlab("Would you feel comfortable discussing a mental health disorder with your coworkers?") + ylab("Count") + theme(axis.title=element_text(size=12), axis.text=element_text(size=10))
+t13 <- ggplot(health, aes(x = health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.coworkers.))+geom_bar()+facet_wrap(health$gender ~., scales="free_y") + ggtitle("Comfort with Discussing Mental Health\nDisorder with Coworkers by Gender") + xlab("Would you feel comfortable discussing a mental health\ndisorder with your coworkers?") + ylab("Count") + theme(axis.title=element_text(size=12), axis.text=element_text(size=10))
 t13
@@
 ```{r}
-t14 <- ggplot(health, aes(x = health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.coworkers.))+geom_bar()+facet_wrap(health$AgeGroup ~., scales="free_y") + ggtitle("Comfort with Discussing MH Disorder with Coworkers by Age Group") + xlab("Would you feel comfortable discussing a mental health disorder with your coworkers?") + ylab("Count") + theme(axis.title=element_text(size=12), axis.text=element_text(size=10))
+t14 <- ggplot(health, aes(x = health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.coworkers.))+geom_bar()+facet_wrap(health$AgeGroup ~., scales="free_y") + ggtitle("Comfort with Discussing Mental Health\nDisorder with Coworkers by Age Group") + xlab("Would you feel comfortable discussing a mental health\ndisorder with your coworkers?") + ylab("Count") + theme(axis.title=element_text(size=12), axis.text=element_text(size=10))
 t14
@@
 ```{r}
-t15 <- ggplot(health, aes(x = health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.coworkers.))+geom_bar()+facet_wrap(health$CompanySize ~., scales="free_y") + ggtitle("Comfort with Discussing MH Disorder with Coworkers by Company Size") + xlab("Would you feel comfortable discussing a mental health disorder with your coworkers?") + ylab("Count") + theme(axis.title=element_text(size=12), axis.text=element_text(size=10))
+t15 <- ggplot(health, aes(x = health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.coworkers.))+geom_bar()+facet_wrap(health$CompanySize ~., scales="free_y") + ggtitle("Comfort with Discussing Mental health\nDisorder with Coworkers by Company Size") + xlab("Would you feel comfortable discussing a mental health\ndisorder with your coworkers?") + ylab("Count") + theme(axis.title=element_text(size=12), axis.text=element_text(size=10))
 t15
@@
 t16 <- ggplot(health, aes(x = health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.coworkers.))+geom_bar()+facet_wrap(health$Have.you.observed.or.experienced.an.unsupportive.or.badly.handled.response.to.a.mental.health.issue.in.your.current.or.previous.workplace.
-~., scales="free_y") + ggtitle("Comfort Disc.
-MH w/ Coworkers by Exp.
-w/ Poor Workplace MH Response") + xlab("Would you feel comfortable discussing a mental health disorder with your coworkers?") + ylab("Count") + theme(axis.title=element_text(size=12), axis.text=element_text(size=10))
+~., scales="free_y") + ggtitle("Comfort with Discussing Mental health disorders\nwith Coworkers by Experience with\npoor Workplace Response\nto mental health") + xlab("Would you feel comfortable discussing a mental health\ndisorder with your coworkers?") + ylab("Count") + theme(axis.title=element_text(size=12), axis.text=element_text(size=10))
 t16
@@
 t17 <- ggplot(health, aes(x = health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.coworkers.))+geom_bar()+facet_wrap(health$Do.you.think.that.team.members.co.workers.would.view.you.more.negatively.if.they.knew.you.suffered.from.a.mental.health.issue.
-~., scales="free_y") + ggtitle("Comfort w/ Disc.
-MH Disorder with Coworkers by Perceived Negative Impact") + xlab("Would you feel comfortable discussing a mental health disorder with your coworkers?") + ylab("Count") + theme(axis.title=element_text(size=12), axis.text=element_text(size=10))
+~., scales="free_y") + ggtitle("Comfort with discussing Mental Health Disorder with\n Coworkers by Perceived Negative Impact") + xlab("Would you feel comfortable discussing a mental health\ndisorder with your coworkers?") + ylab("Count") + theme(axis.title=element_text(size=12), axis.text=element_text(size=10))
 t17
@@
 ```{r}
-ggplot(health, aes(x = health$Do.you.think.that.discussing.a.mental.health.disorder.with.previous.employers.would.have.negative.consequences.)) + geom_bar() + ggtitle("Discussing mental health disorder with previous employer resulting in negative consequences") + xlab("Response") + ylab("Count")
+ggplot(health, aes(x = health$Do.you.think.that.discussing.a.mental.health.disorder.with.previous.employers.would.have.negative.consequences.)) + geom_bar() + ggtitle("Discussing mental health disorder with previous\nemployer resulting in negative consequences") + xlab("Response") + ylab("Count")
 summary(health$Do.you.think.that.discussing.a.mental.health.disorder.with.previous.employers.would.have.negative.consequences.)
@@
 ```{r}
-ggplot(health, aes(x = health$Do.you.think.that.discussing.a.mental.health.disorder.with.your.employer.would.have.negative.consequences.)) + geom_bar() + ggtitle("Discussing mental health disorder with current employer resulting in negative consequences") + xlab("Response") + ylab("Count")
+ggplot(health, aes(x = health$Do.you.think.that.discussing.a.mental.health.disorder.with.your.employer.would.have.negative.consequences.)) + geom_bar() + ggtitle("Discussing mental health disorder with current\nemployer resulting in negative consequences") + xlab("Response") + ylab("Count")
 summary(health$Do.you.think.that.discussing.a.mental.health.disorder.with.your.employer.would.have.negative.consequences.)

### 2018-12-06 Visualizations/Draft Visualizations Template.Rmd
Added colors to two of my charts. Revised slides.

@@
 ```{r}
-t0 <- ggplot(health, aes(x = health$Is.your.anonymity.protected.if.you.choose.to.take.advantage.of.mental.health.or.substance.abuse.treatment.resources.provided.by.your.employer.))+geom_bar()+facet_wrap(~health$CompanySize, scales="free_y") + ggtitle("Perceived Difficulty of Asking for Leave by Gender") + xlab("Perceived Difficulty Level") + ylab("Count")+ theme(axis.title=element_text(size=12))
+t0 <- ggplot(health, aes(x = health$Is.your.anonymity.protected.if.you.choose.to.take.advantage.of.mental.health.or.substance.abuse.treatment.resources.provided.by.your.employer.))+geom_bar(fill="purple")+facet_wrap(~health$CompanySize, scales="free_y") + ggtitle("Anonymity Protections by Comapny Size") + xlab("Perceived Difficulty Level") + ylab("Count")+ theme(axis.title=element_text(size=12))
 t0
@@
 #Create Visualization
-t1 <- ggplot(health, aes(x = health$Is.your.anonymity.protected.if.you.choose.to.take.advantage.of.mental.health.or.substance.abuse.treatment.resources.provided.by.your.employer.))+geom_bar()+facet_wrap(health$TLabel ~ ., scales="free_y") + ggtitle("Anonymity Protections for Tech\nvs.Non-Tech Companies") + xlab("Is your anonymity protected?") + ylab("Count") + theme(axis.title=element_text(size=12))
+t1 <- ggplot(health, aes(x = health$Is.your.anonymity.protected.if.you.choose.to.take.advantage.of.mental.health.or.substance.abuse.treatment.resources.provided.by.your.employer.))+geom_bar(fill="blue")+facet_wrap(health$TLabel ~ ., scales="free_y") + ggtitle("Anonymity Protections for Tech\nvs.Non-Tech Companies") + xlab("Is your anonymity protected?") + ylab("Count") + theme(axis.title=element_text(size=12))
 t1

### 2018-12-06 Visualizations/Draft Visualizations Template.Rmd
Added note at beginning, summary placeholder, and my contribution

@@
 ---
-title: "Draft Visualizations for Semester Project"
+title: "Final Report Semester Project"
 output:
@@
 
+#Introduction
+
+This document contains the fully commented analysis script and outputs, written summary of the project, and summary of contributorship to each part of the project.
+
 #Section 1: Distribution of mental health disorders based on different demographics
@@
 
+#Summary
+
+This is a placeholder for the summary.
+
+#Who did what in the project
+
+Laura - For the work plan, I worked with the group to draft the sections on dataset used, audience, and research questions.
+I also reviewed a list of studies on mental health in the workplace and drafted summaries that can be used as a reference by the group.
+For the data cleaning documentation, I examined nine variables and noted if there were any issues.
+I worked with other group members to determine how to handle the variables.
+For the R Script, I did frequency tables related to my analyses and the variables I examined for data cleaning.
+For the R Plot Draft, I created visualizations and interpretations for my analyses (in section 3, the portions on anonymity policies, ease of taking leave, comfort discussing with coworkers and supervisors).
+For the presentation, I created a template for the presentation that included what was needed and placeholder slides for the analyses the group did.
+I also did slides related to my analysis (anonymity policies, ease of taking leave, comfort discussing with coworkers and supervisors) and used the findings to draft some recommendations.For the final package, I did the first draft of the summary.
+
 #Works Cited

### 2018-12-08 Visualizations/Draft Visualizations Template.Rmd
Cleaned up my analysis

@@
 
-If employees feel that their anonymity is not protected, they may be less likely to reach out for help.
+This part of the analysis looks at answers to the question "Is your anonymity protected if you choose to take advantage of mental health or substance abuse treatment resources provided by your employer?" by reported company size and whether the respondent's company is primarily a tech company.
+This is is important because, if employees feel that their anonymity is not protected, they may be less likely to reach out for help.
 
 ###Anonymity Policies by Company Size
-
-####Crosstab Table
 
@@
 health$CompanySize  = factor(health$How.many.employees.does.your.company.or.organization.have, levels=c("1-5", "6-25", "26-100", "100-500", "500-1000", "More than 1000"))
-#Create Cross-tab Table
-APbCS <- table(health$Is.your.anonymity.protected.if.you.choose.to.take.advantage.of.mental.health.or.substance.abuse.treatment.resources.provided.by.your.employer., health$CompanySize)
-head(APbCS)
-```
-
-####Proportions table
+#Modify Labels for Anonymity Policies
+health$AnonPolicies2 <- factor(health$Is.your.anonymity.protected.if.you.choose.to.take.advantage.of.mental.health.or.substance.abuse.treatment.resources.provided.by.your.employer.,
+levels = c("I don't know", "No", "Yes"),
+labels = c("Don't Know", "No", "Yes"))
+#Create subset
+AnoymityPolicies_By_CompanySize <- table(health$AnonPolicies2, health$CompanySize)
+```
+
+####Crosstab Table
+
+```{r}
+#Print Cross-tab table
+kable(AnoymityPolicies_By_CompanySize)
+```
+
+####Proportions Table
 
@@
 #Create a proportions table by Row
-prop.table(APbCS, 2)
+kable(prop.table(AnoymityPolicies_By_CompanySize, 2))
 ```
@@
 #Do a chi-squared test
-chisq.test(APbCS)
-```
-
-We get a warning that the approximation may be incorrect, likely because some of the values from the table are small.
-Therefore, we cannot draw and conclusions for this test about whether these two variables are related.
-
-####Visualization of Data
-
-```{r}
-t0 <- ggplot(health, aes(x = health$Is.your.anonymity.protected.if.you.choose.to.take.advantage.of.mental.health.or.substance.abuse.treatment.resources.provided.by.your.employer.))+geom_bar(fill="purple")+facet_wrap(~health$CompanySize, scales="free_y") + ggtitle("Anonymity Protections by Comapny Size") + xlab("Perceived Difficulty Level") + ylab("Count")+ theme(axis.title=element_text(size=12))
-t0
+chisq.test(AnoymityPolicies_By_CompanySize)
+```
+
+Our null hypothesis is that there is that company size and anonymity policies are independent.
+Our alternative hypothesis is that there is a relationship between these two variables.
+Because the sensitivity of this test to larger sample sizes we are setting the p value to .01 (Townsley, 2002)
+
+We get a warning that the approximation may be incorrect, likely because some of the values from the table are less than 5 (Townsley, 2002).
+Therefore, we cannot draw any conclusions for this test about whether these two variables are related.
+
+####Visualizing the Data
+
+```{r}
+#Create visualization
+AnoymityPolicies_By_CompanySize_Viz <- ggplot(health, aes(x = health$AnonPolicies2))+geom_bar(fill="purple")+facet_wrap(~health$CompanySize, scales="free_y") + ggtitle("Anonymity Protections by Comapny Size") + xlab("Perceived Difficulty Level") + ylab("Count")+ theme(axis.title=element_text(size=12))
+AnoymityPolicies_By_CompanySize_Viz
 ```
@@
 
-####Cross-tab Table
-
-```{r}
-#Add labels to tech company org
-health$TLabel <- factor(health$Is.your.employer.primarily.a.tech.company.organization.,
+```{r}
+#Add labels to tech company org question
+health$TechCompany2 <- factor(health$Is.your.employer.primarily.a.tech.company.organization.,
 levels = c(0, 1),
 labels = c("Not primarily tech", "Primarily Tech"))
-```
-
-```{r}
-#Create a crosstab table
-APbT2 <- table(health$Is.your.anonymity.protected.if.you.choose.to.take.advantage.of.mental.health.or.substance.abuse.treatment.resources.provided.by.your.employer., health$TLabel)
-head(APbT2)
+#Create a subset
+AnonymityPolicies_by_TechCompany <- table(health$Is.your.anonymity.protected.if.you.choose.to.take.advantage.of.mental.health.or.substance.abuse.treatment.resources.provided.by.your.employer., health$TechCompany2)
+```
+
+####Crosstab Table
+
+```{r}
+#Print Cross-tab table
+kable(AnonymityPolicies_by_TechCompany)
 ```
@@
 #Create a proportions table by Row
-prop.table(APbT2, 2)
+kable(prop.table(AnonymityPolicies_by_TechCompany, 2))
 ```
@@
 #Do a chi-squared test
-chisq.test(APbT2)
-```
-
-This chi-squared test's p value is very large. Therefore, there is likely not a relationship between these two variables.
-
-####Visualization of Data
+chisq.test(AnonymityPolicies_by_TechCompany)
+```
+
+Our null hypothesis is that there is that company size and whether it is primarily a tech company are independent.
+Our alternative hypothesis is that there is a relationship between these two variables.
+Because the sensitivity of this test to larger sample sizes we are setting the p value to .01 (Townsley, 2002).
+This chi-squared test's p value is very large.
+Therefore, we fail to reject the null.
+
+####Visualizing the Data
 
@@
 #Create Visualization
-t1 <- ggplot(health, aes(x = health$Is.your.anonymity.protected.if.you.choose.to.take.advantage.of.mental.health.or.substance.abuse.treatment.resources.provided.by.your.employer.))+geom_bar(fill="blue")+facet_wrap(health$TLabel ~ ., scales="free_y") + ggtitle("Anonymity Protections for Tech\nvs.Non-Tech Companies") + xlab("Is your anonymity protected?") + ylab("Count") + theme(axis.title=element_text(size=12))
-t1
+AnonymityPolicies_by_TechCompany_viz <- ggplot(health, aes(x = health$Is.your.anonymity.protected.if.you.choose.to.take.advantage.of.mental.health.or.substance.abuse.treatment.resources.provided.by.your.employer.))+geom_bar(fill="blue")+facet_wrap(health$TechCompany2 ~ ., scales="free_y") + ggtitle("Anonymity Protections for Tech\nvs.Non-Tech Companies") + xlab("Is your anonymity protected?") + ylab("Count") + theme(axis.title=element_text(size=12))
+AnonymityPolicies_by_TechCompany_viz
 ```
@@
 In both cases, the next most common response to the question is that anonymity is protected for those using mental health services.
-As described above, the fact the majority of respondents do not know their company's anonymity policy is something that has to be addressed.
 
@@
 
+This part of the analysis looks at answers to the question "If a mental health issue prompted you to request a medical leave from work asking for that leave would be" by respondent demographics as well as their reports of several company characteristics.
 This is important because if employees feel that asking for time off from work for medical leave, they may be less likely to seek the help they need.
@@
 ```{r}
-#Modify Labels (ideal if we can get it to fit)
-health$pd2 <- factor(health$If.a.mental.health.issue.prompted.you.to.request.a.medical.leave.from.work..asking.for.that.leave.would.be.,
+#Modify Labels for Perceived Leave Difficulty QUestion (ideal if we can get it to fit)
+health$perceivedleavediff1 <- factor(health$If.a.mental.health.issue.prompted.you.to.request.a.medical.leave.from.work..asking.for.that.leave.would.be.,
 levels = c("Very easy", "Somewhat easy", "Neither easy nor difficult","Somewhat difficult", "Very difficult", "I don't know"),
 labels = c("Very easy (VE)", "Somewhat Easy (SE)", "Neutral (N)", "Somewhat Hard (SH)", "Very Hard (VH)", "Don't Know (DK)"))
-#Modify Labels (if health$pd2 does not fit, use this as an alternate)
-health$pd3 <- factor(health$If.a.mental.health.issue.prompted.you.to.request.a.medical.leave.from.work..asking.for.that.leave.would.be.,
+#Modify Labels for Perceived Leave Difficulty Question (if health$perceivedleavediff1 does not fit, use this as an alternate)
+health$perceivedleavediff2 <- factor(health$If.a.mental.health.issue.prompted.you.to.request.a.medical.leave.from.work..asking.for.that.leave.would.be.,
 levels = c("Very easy", "Somewhat easy", "Neither easy nor difficult","Somewhat difficult", "Very difficult", "I don't know"),
 labels = c("VE", "SE", "N", "SH", "VH", "DK"))
-```
-
-```{r}
-#Crosstab table
-ELDbG <- table(health$pd2, health$gender)
-ELDbG
-prop.table(ELDbG, 2)
-```
-
-####Chi-Squared
-
-We get a warning that the approximation may be incorrect, likely because some of the values from the table are small.
-However, it potentially indicates that that the differences between genders may not be statistically significant (or we do not have enough information)
-
-```{r}
-chisq.test(ELDbG)
-```
-
-####Visualization of Data
+#Create a subset
+LeaveDiffbyGender <- table(health$perceivedleavediff1, health$gender)
+```
+
+####Crosstab Table
+```{r}
+#Print Crosstab
+kable(LeaveDiffbyGender)
+```
+
+####Proportions Table
+```{r}
+#Create Proportions table
+kable(prop.table(LeaveDiffbyGender, 2))
+```
+
+####Chi-Squared
+
+```{r}
+#Run chi-squared test
+chisq.test(LeaveDiffbyGender)
+```
+
+Our null hypothesis is that there is that gender and perceived difficulty of requesting leave are independent.
+Our alternative hypothesis is that there is a relationship between these two variables.
+Because the sensitivity of this test to larger sample sizes we are setting the p value to .01 (Townsley, 2002)
+
+We get a warning that the approximation may be incorrect, likely because some of the values from the table are less than 5 (Townsley, 2002).
+However, the large p value potentially indicates that that the differences between genders may not be statistically significant (or we do not have enough information because of the small number of people of other genders in our dataset).
+
+####Visualizing the Data
 
@@
 #Create Visualization
-t2 <- ggplot(health, aes(x = health$pd3))+geom_bar()+facet_wrap(health$gender ~ ., scales="free_y") + ggtitle("Perceived Difficulty of Asking for Leave by Gender") + xlab("Perceived Difficulty Level") + ylab("Count") + theme(axis.title=element_text(size=12))
-t2
-```
+LeaveDiffbyGender_Viz <- ggplot(health, aes(x = health$perceivedleavediff2))+geom_bar(fill="orange")+facet_wrap(health$gender ~ ., scales="free_y") + ggtitle("Perceived Difficulty of Asking for Leave by Gender") + xlab("Perceived Difficulty Level") + ylab("Count") + theme(axis.title=element_text(size=12))
+LeaveDiffbyGender_Viz
+```
+
 NOTE:  VE = Very Easy, SE = Somewhat Easy, N = Neutral (or Neither Easy nor Difficult), SH = Somewhat Hard, VH = Very Hard, DK = Don't Know.
@@
 Interestingly, for women the second most common answer is "Somewhat Difficult", while for men the second most common answer is "Very Easy."  For those indicating their gender falls into another category, an equal amount indicated that they felt asking for leave was very hard or provided a neutral response ("neither easy or hard").
-Across all genders there is a significant group of people indicating they find it somewhat to very hard to ask for leave.
-That being said, there are fewer women and those from other genders participating in this survey (compared to men), which may impact our results.
-Furthermore, the chi-squared test indicated that the approximation may be incorrect, likely because some of the values from the table are small.
+Across all genders there is a sizable group of people indicating they find it somewhat to very hard to ask for leave, which indicates that perceived difficulty may vary by company.
+That being said, there are fewer women and those from other genders participating in this survey (compared to men).
+This means that we may not have a complete picture of the opinions of women and those who state their gender as other than male or female.
 
@@
 health$AgeGroup <- cut(health$age, breaks = c(seq(17, 74, by = 20), Inf), labels = labs, right = FALSE)
-```
-
-```{r}
-#Crosstab table
-ELDbA <- table(health$pd2, health$AgeGroup)
-ELDbA
-#Proportions table
-prop.table(ELDbA)
-```
-
-####Chi-Squared
-
-```{r}
-chisq.test(ELDbA)
-```
-
-We get a warning that the approximation may be incorrect, likely because some of the values from the table are small.
-However, it potentially indicates that that the differences between age groups may not be statistically significant (or we do not have enough information)
-
-####Visualization of Data
+#Create dataframe
+LeaveDiffbyAge <- table(health$perceivedleavediff1, health$AgeGroup)
+```
+
+####Crosstab Table
+
+```{r}
+#Print Crosstab table
+kable(LeaveDiffbyAge)
+```
+
+####Proportions Table
+```{r}
+#Create Proportions table
+kable(prop.table(LeaveDiffbyAge, 2))
+```
+
+####Chi-Squared
+
+```{r}
+chisq.test(LeaveDiffbyAge)
+```
+
+Our null hypothesis is that there is that age group and perceived difficulty of requesting leave are independent.
+Our alternative hypothesis is that there is a relationship between these two variables.
+Because the sensitivity of this test to larger sample sizes we are setting the p value to .01 (Townsley, 2002)
+
+We get a warning that the approximation may be incorrect, likely because because of the small number of respondents in our survey in the 57-77 age group (Townsley, 2002).
+However, the large p value potentially indicates that that the differences in perceived ease of requesting leave between age may not be statistically significant (or we do not have enough information because of the small number of people in the 57-77 age group in our dataset).
+
+####Visualizing the Data
 
@@
 #Create Visualization
-t3 <- ggplot(health, aes(x = health$pd3))+geom_bar()+facet_wrap(health$AgeGroup ~ ., scales="free_y") + ggtitle("Perceived Difficulty of Asking for Leave by Age Group") + xlab("Perceived Difficulty Level") + ylab("Count") + theme(axis.title=element_text(size=12))
-t3
-```
+LeaveDiffbyAge_Viz <- ggplot(health, aes(x = health$perceivedleavediff2))+geom_bar(fill = "orange")+facet_wrap(health$AgeGroup ~ ., scales="free_y") + ggtitle("Perceived Difficulty of Asking for Leave by Age Group") + xlab("Perceived Difficulty Level") + ylab("Count") + theme(axis.title=element_text(size=12))
+LeaveDiffbyAge_Viz
+```
+
 NOTE:  VE = Very Easy, SE = Somewhat Easy, N = Neutral (or Neither Easy nor Difficult), SH = Somewhat Hard, VH = Very Hard, DK = Don't Know.
@@
 That being said, there are few people who are 57-77 participating in this survey and there are fewer people in the 37-57 age group than the 17-27 age group.
-Furthermore, the chi-squared test indicated that the approximation may be incorrect, likely because some of the values from the table are small (since few people fell into the 57-77 age range).
+Therefore, we may not have a complete picture of how perceived ease of requesting leave for a mental health issue may change as people age.
 
@@
 ```{r}
-#Crosstab table
-ELDbCS <- table(health$pd2, health$CompanySize)
-ELDbCS
-prop.table(ELDbCS, 2)
-```
-
-####Chi-Squared
-
-```{r}
-chisq.test(ELDbCS)
-```
-
+#Create subset
+LeaveDiffbyCompanySize <- table(health$perceivedleavediff1, health$CompanySize)
+```
+
+####Crosstab Table
+
+```{r}
+#Print Crosstab Table
+kable(LeaveDiffbyCompanySize)
+```
+
+####Proportions Table
+
+```{r}
+kable(prop.table(LeaveDiffbyCompanySize, 2))
+```
+
+####Chi-Squared
+
+```{r}
+chisq.test(LeaveDiffbyCompanySize)
+```
+
+Our null hypothesis is that there is that company size and perceived difficulty of requesting leave are independent.
+Our alternative hypothesis is that there is a relationship between these two variables.
+Because the sensitivity of this test to larger sample sizes we are setting the p value to .01 (Townsley, 2002).
 Because the p value is less than .01 we can reject the null and say that we think that there is a relationship between these two variables.
 
-####Visualization of Data
+####Visualizing the Data
 
@@
 #Create Visualization
-t4 <- ggplot(health, aes(x = health$pd3))+geom_bar()+facet_wrap(health$CompanySize~ ., scales="free_y") + ggtitle("Perceived Difficulty of Asking for Leave\nby Company Size") + xlab("Perceived Difficulty Level") + ylab("Count")
-t4
-```
+LeaveDiffbyCompanySize_viz <- ggplot(health, aes(x = health$perceivedleavediff2))+geom_bar(fill = "orange")+facet_wrap(health$CompanySize~ ., scales="free_y") + ggtitle("Perceived Difficulty of Asking for Leave\nby Company Size") + xlab("Perceived Difficulty Level") + ylab("Count")
+LeaveDiffbyCompanySize_viz
+```
+
 NOTE:  VE = Very Easy, SE = Somewhat Easy, N = Neutral (or Neither Easy nor Difficult), SH = Somewhat Hard, VH = Very Hard, DK = Don't Know.
@@
 ```{r}
-#Modify Labels for mental health benefit provision
-health$mhb2 <- factor(health$Does.your.employer.provide.mental.health.benefits.as.part.of.healthcare.coverage.,
+#Modify Labels for mental health benefit provision question
+health$MHBenefit2 <- factor(health$Does.your.employer.provide.mental.health.benefits.as.part.of.healthcare.coverage.,
 levels = c("I don't know", "No", "Not eligible for coverage / N/A","Yes"),
 labels = c("Don't Know", "No", "Ineligible/NA", "Yes"))
-```
-
-```{r}
-#Crosstab Table
-ELDbMHB <- table(health$pd2, health$mhb2)
-ELDbMHB
-```
-
-####Chi-Squared
-
-```{r}
-chisq.test(ELDbMHB)
-```
-
-Because the p value is not less than .01 we cannot reject the null. The null hypothesis is that there is no relationship between these two variables.
-
-####Create Visualization
-
-```{r}
-t5 <- ggplot(health, aes(x = health$pd3))+geom_bar()+facet_wrap(~ health$mhb2, scales="free_y") + ggtitle("Perceived Difficulty of Asking for Leave by Mental\nHealth Benefit Provision") + xlab("Perceived Difficulty Level") + ylab("Count") + theme(axis.title=element_text(size=12))
-t5
-```
+#Create the subset
+LeaveDiffbyMHBenefit <- table(health$perceivedleavediff1, health$MHBenefit2)
+```
+
+####Crosstab Table
+
+```{r}
+#Print the Crosstab Table
+kable(LeaveDiffbyMHBenefit)
+```
+
+####Proportions Table
+
+```{r}
+#Print the Crosstab Table
+kable(prop.table(LeaveDiffbyMHBenefit, 2))
+```
+
+####Chi-Squared
+
+```{r}
+#Run Chi-squared test
+chisq.test(LeaveDiffbyMHBenefit)
+```
+
+Our null hypothesis is that there is that reported mental health benefit provision and perceived difficulty of requesting leave are independent.
+Our alternative hypothesis is that there is a relationship between these two variables.
+Because the sensitivity of this test to larger sample sizes we are setting the p value to .01 (Townsley, 2002).
+Because the p value is above .01, we fail to reject the null. There does not appear to be a statistically significant relationship between the two variables.
+
+####Visualizing the Data
+
+```{r}
+#Create Visualization
+LeaveDiffbyMHBenefit_viz <- ggplot(health, aes(x = health$perceivedleavediff2))+geom_bar(fill = "dark green")+facet_wrap(~ health$MHBenefit2, scales="free_y") + ggtitle("Perceived Difficulty of Asking for Leave by Mental\nHealth Benefit Provision") + xlab("Perceived Difficulty Level") + ylab("Count") + theme(axis.title=element_text(size=12))
+LeaveDiffbyMHBenefit_viz
+```
+
 NOTE:  VE = Very Easy, SE = Somewhat Easy, N = Neutral (or Neither Easy nor Difficult), SH = Somewhat Hard, VH = Very Hard, DK = Don't Know.
@@
 ```{r}
-ELDbEDM <- table(health$pd2, health$Has.your.employer.ever.formally.discussed.mental.health..for.example..as.part.of.a.wellness.campaign.or.other.official.communication..)
-ELDbEDM
-```
-
-####Chi-Squared
-
-```{r}
-chisq.test(ELDbEDM)
-```
-
-Because the p value is less than .01 we can reject the null and say that we think that there is a relationship between these two variables.
-
-####Create Visualization
-
-```{r}
-t6 <- ggplot(health, aes(x = health$pd3))+geom_bar()+facet_wrap( health$Has.your.employer.ever.formally.discussed.mental.health..for.example..as.part.of.a.wellness.campaign.or.other.official.communication..
-~., scales="free_y") + ggtitle("Perceived Difficulty of Asking for Leave by Mental Health\nDiscussion by Employer") + xlab("Perceived Difficulty Level") + ylab("Count") + theme(axis.title=element_text(size=12))
-t6
-```
+#Create the subset
+LeaveDiffbyMHDiscussion <- table(health$perceivedleavediff1, health$Has.your.employer.ever.formally.discussed.mental.health..for.example..as.part.of.a.wellness.campaign.or.other.official.communication..)
+```
+
+####Crosstab Table
+
+```{r}
+#Print crosstab table
+kable(LeaveDiffbyMHDiscussion)
+```
+
+####Proportions Table
+
+```{r}
+#Create proportions table
+kable(prop.table(LeaveDiffbyMHDiscussion, 2))
+```
+
+####Chi-Squared
+
+```{r}
+#Run chi-squared test
+chisq.test(LeaveDiffbyMHDiscussion)
+```
+
+Our null hypothesis is that there is that reported mental health discussion by current employer and perceived difficulty of requesting leave are independent.
+Our alternative hypothesis is that there is a relationship between these two variables.
+Because the sensitivity of this test to larger sample sizes we are setting the p value to .01 (Townsley, 2002).
+Because the p value is below .01, we reject the null.
+There appears to be a statistically significant relationship between the two variables.
+
+####Visualizing the Data
+
+```{r}
+#Create Visualization
+LeaveDiffbyMHDiscussion_viz <- ggplot(health, aes(x = health$perceivedleavediff2))+geom_bar(fill = "dark green")+facet_wrap( health$Has.your.employer.ever.formally.discussed.mental.health..for.example..as.part.of.a.wellness.campaign.or.other.official.communication..
+~., scales="free_y") + ggtitle("Perceived Difficulty of Asking for \nLeave by Mental Health\nDiscussion by Employer") + xlab("Perceived Difficulty Level") + ylab("Count") + theme(axis.title=element_text(size=12))
+LeaveDiffbyMHDiscussion_viz
+```
+
 NOTE:  VE = Very Easy, SE = Somewhat Easy, N = Neutral (or Neither Easy nor Difficult), SH = Somewhat Hard, VH = Very Hard, DK = Don't Know.
@@
 For those where there has been a discussion, far fewer people say it would be hard to request leave to handle a mental illness than those who say it would be easy to very easy.
-For those where there has not been a discussion (which is the majority of respondents), the second most common answer is that it would be somewhat hard to request leave to hanlde a mental illness.
+For those where there has not been a discussion (which is the majority of respondents), the second most common answer is that it would be somewhat hard to request leave to handle a mental illness.
+In addition, the proportion of respondents who indicated that it would be very hard to ask for leave is a lot lower in companies where it is reported that there was a mental health discussion or that it is unknown that there has been a mental health discussion compared to companies where there has not been a discussion.
 
@@
 ```{r}
-ELDbEOR <- table(health$pd2, health$Does.your.employer.offer.resources.to.learn.more.about.mental.health.concerns.and.options.for.seeking.help.)
-ELDbEOR
-```
-
-####Chi-Squared
-
-Because the p value is less than .01 we can reject the null and say that we think that there are differences between categories.
-
-```{r}
-chisq.test(ELDbEOR)
-```
-
-####Create Visualization
-
-```{r}
-t7 <- ggplot(health, aes(x = health$pd3))+geom_bar()+facet_wrap( health$Does.your.employer.offer.resources.to.learn.more.about.mental.health.concerns.and.options.for.seeking.help.
+#Creating the subset
+LeaveDiffbyOtherMHResources <- table(health$perceivedleavediff1, health$Does.your.employer.offer.resources.to.learn.more.about.mental.health.concerns.and.options.for.seeking.help.)
+```
+
+####Crosstab Table
+
+```{r}
+#Print the crosstab
+kable(LeaveDiffbyOtherMHResources)
+```
+
+####Proportions Table
+
+```{r}
+#Create the proportions table
+kable(prop.table(LeaveDiffbyOtherMHResources, 2))
+```
+
+####Chi-Squared
+
+```{r}
+#Run chi-squared test
+chisq.test(LeaveDiffbyOtherMHResources)
+```
+
+Our null hypothesis is that there is that reported other mental health resources by current employer and perceived difficulty of requesting leave are independent.
+Our alternative hypothesis is that there is a relationship between these two variables.
+Because the sensitivity of this test to larger sample sizes we are setting the p value to .01 (Townsley, 2002).
+Because the p value is below .01, we reject the null.
+There appears to be a statistically significant relationship between the two variables.
+
+####Visualizing the Data
+
+```{r}
+#Create visualization
+LeaveDiffbyOtherMHResources_viz <- ggplot(health, aes(x = health$perceivedleavediff2))+geom_bar(fill = "dark green")+facet_wrap( health$Does.your.employer.offer.resources.to.learn.more.about.mental.health.concerns.and.options.for.seeking.help.
 ~., scales="free_y") + ggtitle("Perceived Difficulty of Asking for Leave by Mental\nHealth Resource Provision") + xlab("Perceived Difficulty Level") + ylab("Count") + theme(axis.title=element_text(size=12))
-t7
-```
+LeaveDiffbyOtherMHResources_viz
+```
+
 NOTE:  VE = Very Easy, SE = Somewhat Easy, N = Neutral (or Neither Easy nor Difficult), SH = Somewhat Hard, VH = Very Hard, DK = Don't Know.
@@
 ```{r}
-ELDbPR <- table(health$pd2, health$Have.you.observed.or.experienced.an.unsupportive.or.badly.handled.response.to.a.mental.health.issue.in.your.current.or.previous.workplace.)
-ELDbPR
-prop.table(ELDbPR, 2)
-```
-
-#Revise Labels
-
-```{r}
-#Modify Labels for unsupportive response to make them shorter
-health$epr <- factor(health$Have.you.observed.or.experienced.an.unsupportive.or.badly.handled.response.to.a.mental.health.issue.in.your.current.or.previous.workplace.,
+#Modify Labels for poor response to mental health issue question to make them shorter
+health$expwpoorMHresponse <- factor(health$Have.you.observed.or.experienced.an.unsupportive.or.badly.handled.response.to.a.mental.health.issue.in.your.current.or.previous.workplace.,
 levels = c("Maybe/Not sure", "N/A", "No","Yes, I experienced", "Yes, I observed"),
 labels = c("Don't Know", "N/A", "No", "Yes, experienced", "Yes, observed"))
-table(health$pd2, health$epr)
-```
-
-####Chi-Squared
-
-```{r}
-chisq.test(ELDbPR)
-```
-
-Because the p value is less than .01 we can reject the null and say that we think that there are differences between categories.
-
-####Create Visualization
-
-```{r}
-t8 <- ggplot(health, aes(x = health$pd3))+geom_bar()+facet_wrap(health$epr ~., scales="free_y") + ggtitle("Perceived Difficulty of Asking for Leave by Experience\nwith Poor Mental health Response") + xlab("Perceived Difficulty Level") + ylab("Count") + theme(axis.title=element_text(size=12))
-t8
-```
+#Create subset
+LeaveDiffbyPoorResponse <- table(health$perceivedleavediff1, health$expwpoorMHresponse)
+```
+
+####Crosstab Table
+
+```{r}
+#Create table
+kable(LeaveDiffbyPoorResponse)
+```
+
+####Proportions Table
+
+```{r}
+#Create proportions table
+kable(prop.table(LeaveDiffbyPoorResponse, 2))
+```
+
+####Chi-Squared
+
+```{r}
+chisq.test(LeaveDiffbyPoorResponse)
+```
+
+Our null hypothesis is that there is that experience with a poor response to a mental health issue (current or former workplace) and perceived difficulty of requesting leave are independent.
+Our alternative hypothesis is that there is a relationship between these two variables.
+Because the sensitivity of this test to larger sample sizes we are setting the p value to .01 (Townsley, 2002).
+Because the p value is below .01, we reject the null.
+There appears to be a statistically significant relationship between the two variables.
+
+####Visualizing the Data
+
+```{r}
+#Create Visualization
+LeaveDiffbyPoorResponse_viz <- ggplot(health, aes(x = health$perceivedleavediff2))+geom_bar(fill = "red")+facet_wrap(health$expwpoorMHresponse ~., scales="free_y") + ggtitle("Perceived Difficulty of Asking for Leave by Experience\nwith Poor Mental health Response") + xlab("Perceived Difficulty Level") + ylab("Count") + theme(axis.title=element_text(size=12))
+LeaveDiffbyPoorResponse_viz
+```
+
 NOTE:  E = Very Easy, S = Somewhat Easy, N = Neutral (or Neither Easy nor Difficult), SH = Somewhat Hard, H = Very Hard, D = Don't Know.
@@
 
+This part of the analysis looks at answers to the question "Would you feel comfortable discussing a mental health disorder with your direct supervisor" by respondent demographics as well as their reports of several company characteristics.
 This is important because if an employee has a mental health issue, they should ideally be comfortable discussing it with a supervisor in case they need additional assistance.
-In addition, we may want to consider training supervisors on how to handle instances where employees reach out to them about mental health.
 
@@
 ```{r}
-MHbG <- table(health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.direct.supervisor.s.., health$gender)
-MHbG
-prop.table(MHbG, 2)
-```
-
-####Chi-Squared
-
-```{r}
-chisq.test(MHbG)
-```
-
-The p value is very large.  Therefore, we cannot reject the null hypothesis. The null hypothesis is that these two variables are indepdendent (no relationship between them)
-
-####Create Visualization
-
-```{r}
-t9 <- ggplot(health, aes(x = health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.direct.supervisor.s..))+geom_bar()+facet_grid(~ health$gender) + ggtitle("Comfort with Discussing Mental Health\nDisorder with Supervisor by Gender") + xlab("Would you feel comfortable discussing a mental health\ndisorder with your supervisor?") + ylab("Count") + theme(axis.title=element_text(size=12), axis.text=element_text(size=10))
-t9
+#Create subset
+DiscMHBossbyGender <- table(health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.direct.supervisor.s.., health$gender)
+```
+
+####Crosstab Table
+
+```{r}
+#Create crosstab
+kable(DiscMHBossbyGender)
+```
+
+####Proportions Table
+
+```{r}
+#Create proportion table
+kable(prop.table(DiscMHBossbyGender, 2))
+```
+
+####Chi-Squared
+
+```{r}
+#Run chi-squared test
+chisq.test(DiscMHBossbyGender)
+```
+
+Our null hypothesis is that there is that reported comfort discussing mental health with supervisor and gender are independent.
+Our alternative hypothesis is that there is a relationship between these two variables.
+Because the sensitivity of this test to larger sample sizes we are setting the p value to .01 (Townsley, 2002).
+Because the p value is very large, we fail to reject the null.
+There does not appear to be a statistically significant relationship between the two variables.
+However, this might be influenced by the small frequencies among those who report having an other gender (Townsley, 2002).
+
+####Visualizing the Data
+
+```{r}
+#Create visualization
+DiscMHBossbyGender_viz <- ggplot(health, aes(x = health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.direct.supervisor.s..))+geom_bar(fill = "orange")+facet_wrap(~ health$gender, scales="free_y") + ggtitle("Comfort with Discussing Mental Health\nDisorder with Supervisor by Gender") + xlab("Would you feel comfortable discussing a mental health\ndisorder with your supervisor?") + ylab("Count") + theme(axis.title=element_text(size=12), axis.text=element_text(size=10))
+DiscMHBossbyGender_viz 
 ```
@@
 ```{r}
-MHbA <- table(health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.direct.supervisor.s.., health$AgeGroup)
-MHbA
-prop.table(MHbA, 2)
-```
-
-####Chi-Squared
-
-```{r}
-chisq.test(MHbA)
-```
-
-We get a warning that the approximation may be incorrect, likely because some of the values from the table are small.
-However, it potentially indicates that that the differences between age groups may not be statistically significant (or we do not have enough information).
-
-####Create Visualization
-
-```{r}
-t10 <- ggplot(health, aes(x = health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.direct.supervisor.s..))+geom_bar()+facet_wrap(health$AgeGroup ~., scales="free_y") + ggtitle("Comfort with Discussing Mental Health\n Disorder with Supervisor by Age") + xlab("Would you feel comfortable discussing a mental health\ndisorder with your supervisor?") + ylab("Count") + theme(axis.title=element_text(size=12), axis.text=element_text(size=10))
-t10
+#Create subset
+DiscMHBossbyAge <- table(health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.direct.supervisor.s.., health$AgeGroup)
+```
+
+####Crosstab Table
+
+```{r}
+#Run crosstab table
+kable(DiscMHBossbyAge)
+```
+
+####Proportions Table
+
+```{r}
+kable(prop.table(DiscMHBossbyAge, 2))
+```
+
+####Chi-Squared
+
+```{r}
+chisq.test(DiscMHBossbyAge)
+```
+
+Our null hypothesis is that there is that age group and perceived difficulty of requesting leave are independent.
+Our alternative hypothesis is that there is a relationship between these two variables.
+Because the sensitivity of this test to larger sample sizes we are setting the p value to .01 (Townsley, 2002)
+
+We get a warning that the approximation may be incorrect, likely because because of the small number of respondents in our survey in the 57-77 age group (Townsley, 2002).
+However, the large p value indicates that that the differences in perceived ease of requesting leave between age may not be statistically significant (or we do not have enough information because of the small number of people in the 57-77 age group in our dataset).
+
+####Visualizing the Data
+
+```{r}
+DiscMHBossbyAge_viz <- ggplot(health, aes(x = health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.direct.supervisor.s..))+geom_bar(fill = "orange")+facet_wrap(health$AgeGroup ~., scales="free_y") + ggtitle("Comfort with Discussing Mental Health\n Disorder with Supervisor by Age") + xlab("Would you feel comfortable discussing a mental health\ndisorder with your supervisor?") + ylab("Count") + theme(axis.title=element_text(size=12), axis.text=element_text(size=10))
+DiscMHBossbyAge_viz
 ```
@@
 ```{r}
-MHbCS <- table(health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.direct.supervisor.s.., health$CompanySize)
-MHbCS
-prop.table(MHbCS, 2)
-```
-
-####Chi-Squared
-```{r}
-chisq.test(MHbCS)
-```
-
-Because the p value is not less than .01 we cannot reject the null. The null hypothesis is that there is no relationship between these two variables.
-
-####Create Visualization
-
-```{r}
-t11 <- ggplot(health, aes(x = health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.direct.supervisor.s..))+geom_bar()+facet_wrap(health$CompanySize ~., scales="free_y") + ggtitle("Comfort with Discussion of Mental Health\nDisorder with Supervisor by Company Size") + xlab("Would you feel comfortable discussing a mental health\ndisorder with your supervisor?") + ylab("Count") + theme(axis.title=element_text(size=12), axis.text=element_text(size=10))
-t11
+#Creating subset
+DiscMHBossbyCompSize <- table(health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.direct.supervisor.s.., health$CompanySize)
+```
+
+####Crosstab Table
+
+```{r}
+#Creating the crosstab
+kable(DiscMHBossbyCompSize)
+```
+
+####Proportions Table
+
+```{r}
+#Create the proportions table
+kable(prop.table(DiscMHBossbyCompSize, 2))
+```
+
+####Chi-Squared
+```{r}
+#Run chi-squared test
+chisq.test(DiscMHBossbyCompSize)
+```
+
+Our null hypothesis is that there is that reported comfort discussing mental health with supervisor and reported company size are independent.
+Our alternative hypothesis is that there is a relationship between these two variables.
+Because the sensitivity of this test to larger sample sizes we are setting the p value to .01 (Townsley, 2002).
+Because the p value is not less than .01 we cannot reject the null.
+
+####Visualizing the Data
+
+```{r}
+#Create visualization
+DiscMHBossbyCompSize_viz <- ggplot(health, aes(x = health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.direct.supervisor.s..))+geom_bar(fill = "purple")+facet_wrap(health$CompanySize ~., scales="free_y") + ggtitle("Comfort with Discussion of Mental Health\nDisorder with Supervisor by Company Size") + xlab("Would you feel comfortable discussing a mental health\ndisorder with your supervisor?") + ylab("Count") + theme(axis.title=element_text(size=12), axis.text=element_text(size=10))
+DiscMHBossbyCompSize_viz
 ```
@@
 ```{r}
-MHbPR <- table(health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.direct.supervisor.s.., health$Have.you.observed.or.experienced.an.unsupportive.or.badly.handled.response.to.a.mental.health.issue.in.your.current.or.previous.workplace.)
-MHbPR
-prop.table(MHbPR, 2)
-```
-
-####Chi-Squared
-
-```{r}
-chisq.test(MHbPR)
-```
-
-####Create Visualization
-
-```{r}
-t17 <- ggplot(health, aes(x = health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.direct.supervisor.s..))+geom_bar()+facet_wrap(health$Have.you.observed.or.experienced.an.unsupportive.or.badly.handled.response.to.a.mental.health.issue.in.your.current.or.previous.workplace.
-~., scales="free_y") + ggtitle("Comfort with Discussing Mental Health with\nSupervisor by Experience with Poor Workplace Response") + xlab("Would you feel comfortable discussing a mental health\ndisorder with your supervisor?") + ylab("Count") + theme(axis.title=element_text(size=12), axis.text=element_text(size=10))
-t17
+#Create subset
+DiscMHBossbyPoorResponse1 <- table(health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.direct.supervisor.s.., health$Have.you.observed.or.experienced.an.unsupportive.or.badly.handled.response.to.a.mental.health.issue.in.your.current.or.previous.workplace.)
+```
+
+####Crosstab Table
+
+```{r}
+#Create crosstab table
+kable(DiscMHBossbyPoorResponse1)
+```
+
+####Proportions Table
+
+```{r}
+#Create proportions table
+kable(prop.table(DiscMHBossbyPoorResponse1, 2))
+```
+
+####Chi-Squared
+
+```{r}
+#Run chi-squared test
+chisq.test(DiscMHBossbyPoorResponse1)
+```
+
+Our null hypothesis is that there is that reported comfort discussing mental health with supervisor and experience with a poor response to a mental health issue are independent.
+Our alternative hypothesis is that there is a relationship between these two variables.
+Because the sensitivity of this test to larger sample sizes we are setting the p value to .01 (Townsley, 2002).
+Because the p value is less than .01 we can reject the null and state that we suspect that there is a relationship between these two variables.
+
+####Visualizing the Data
+
+```{r}
+#Create visualization
+DiscMHBossbyPoorResponse1_viz <- ggplot(health, aes(x = health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.direct.supervisor.s..))+geom_bar(fill = "red")+facet_wrap(health$Have.you.observed.or.experienced.an.unsupportive.or.badly.handled.response.to.a.mental.health.issue.in.your.current.or.previous.workplace.
+~., scales="free_y") + ggtitle("Comfort with Discussing Mental Health with\nSupervisor by Experience \nwith Poor Workplace Response") + xlab("Would you feel comfortable discussing a mental health\ndisorder with your supervisor?") + ylab("Count") + theme(axis.title=element_text(size=12), axis.text=element_text(size=10))
+DiscMHBossbyPoorResponse1_viz
 ```
@@
 ```{r}
-MHbVN <- table(health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.direct.supervisor.s.., health$Do.you.think.that.discussing.a.mental.health.disorder.with.your.employer.would.have.negative.consequences.)
-MHbVN
-```
-
-####Chi-Squared
-
-```{r}
-chisq.test(MHbVN)
-```
-
-Because the p value is less than .01 we can reject the null and say that we think that there is a statistically significant relationship between these two categories.
-
-####Create Visualization
-
-```{r}
 #Modify Labels for perception of mental health disclosure impact
@@
 levels = c("Maybe", "No", "Yes"),
-labels = c("Maybe Expect a Negative Impact", "Do Not Expect Negative Impact", "Expect Negative Impact"))
-#Check Results
-table(health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.direct.supervisor.s.., health$negimp)
-```
-
-```{r}
-t12 <- ggplot(health, aes(x = health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.direct.supervisor.s..))+geom_bar()+facet_wrap(health$negimp ~., scales="free_y") + ggtitle("Comfort with Discussing Mental Health disorder\nwith Supervisor by Perception of Negative Impact") + xlab("Would you feel comfortable discussing a mental health disorder\nwith your supervisor?") + ylab("Count") + theme(axis.title=element_text(size=12), axis.text=element_text(size=10))
-t12
+labels = c("Maybe Expect Impact", "Do Not Expect Impact", "Expect Impact"))
+#create subset
+DiscMHBossbyNegImpact <- table(health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.direct.supervisor.s.., health$negimp)
+```
+
+####Crosstab Table
+
+```{r}
+kable(DiscMHBossbyNegImpact)
+```
+
+####Proportions Table
+
+```{r}
+kable(prop.table(DiscMHBossbyNegImpact, 2))
+```
+
+####Chi-Squared
+
+```{r}
+chisq.test(DiscMHBossbyNegImpact)
+```
+
+Our null hypothesis is that there is that reported comfort discussing mental health with supervisor and perception that disclosing a mental health disorder to employer would have a negative impact on career are independent.
+Our alternative hypothesis is that there is a relationship between these two variables.
+Because the sensitivity of this test to larger sample sizes we are setting the p value to .01 (Townsley, 2002).
+Because the p value is less than .01 we can reject the null and state that we suspect that there is a relationship between these two variables.
+
+####Visualizing the Data
+
+```{r}
+DiscMHBossbyNegImpact_viz <- ggplot(health, aes(x = health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.direct.supervisor.s..))+geom_bar(fill = "red")+facet_wrap(health$negimp ~., scales="free_y") + ggtitle("Comfort with Discussing Mental Health disorder\nwith Supervisor by Perception of Negative Impact") + xlab("Would you feel comfortable discussing a mental health disorder\nwith your supervisor?") + ylab("Count") + theme(axis.title=element_text(size=12), axis.text=element_text(size=10))
+DiscMHBossbyNegImpact_viz
 ```
@@
 
+This part of the analysis looks at answers to the question "Would you feel comfortable discussing a mental health disorder with your coworkers" by respondent demographics as well as their reports of several company characteristics.
 This is important because if an employee has a mental health issue, they should ideally be comfortable discussing it with a coworkers in case they need additional assistance.
@@
 ```{r}
-MHCbG <- table(health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.coworkers., health$gender)
-MHCbG
-prop.table(MHCbG, 2)
-```
-
-####Chi-Squared
-
-```{r}
-chisq.test(MHCbG)
-```
-
-The chi-squared is very large.  Therefore, we cannot reject the null hypothesis that these categories are independent.
-
-####Create Visualization
-
-```{r}
-t13 <- ggplot(health, aes(x = health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.coworkers.))+geom_bar()+facet_wrap(health$gender ~., scales="free_y") + ggtitle("Comfort with Discussing Mental Health\nDisorder with Coworkers by Gender") + xlab("Would you feel comfortable discussing a mental health\ndisorder with your coworkers?") + ylab("Count") + theme(axis.title=element_text(size=12), axis.text=element_text(size=10))
-t13
+#Create subset
+DiscMHCoworkerbyGender <- table(health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.coworkers., health$gender)
+```
+
+####Crosstab Table
+
+```{r}
+kable(DiscMHCoworkerbyGender)
+```
+
+####Proportions Table
+
+```{r}
+kable(prop.table(DiscMHCoworkerbyGender, 2))
+```
+
+####Chi-Squared
+
+```{r}
+chisq.test(DiscMHCoworkerbyGender)
+```
+
+Our null hypothesis is that there is that reported comfort discussing mental health with coworkers and gender are independent.
+Our alternative hypothesis is that there is a relationship between these two variables.
+Because the sensitivity of this test to larger sample sizes we are setting the p value to .01 (Townsley, 2002).
+The chi-squared is very large.
+Therefore, we cannot reject the null hypothesis that these categories are independent.
+
+####Visualizing the Data
+
+```{r}
+DiscMHCoworkerbyGender_viz <- ggplot(health, aes(x = health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.coworkers.))+geom_bar(fill = "orange")+facet_wrap(health$gender ~., scales="free_y") + ggtitle("Comfort with Discussing Mental Health\nDisorder with Coworkers by Gender") + xlab("Would you feel comfortable discussing a mental health\ndisorder with your coworkers?") + ylab("Count") + theme(axis.title=element_text(size=12), axis.text=element_text(size=10))
+DiscMHCoworkerbyGender_viz
 ```
@@
 ```{r}
-MHCbA <- table(health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.coworkers., health$AgeGroup)
-MHCbA
-#Proportions (as column percentages)
-prop.table(MHCbA, 2)
-```
-
-####Chi-Squared
-
-```{r}
-chisq.test(MHCbA)
-```
-
-We get a warning that the approximation may be incorrect, likely because some of the values from the table are small.
-However, it potentially indicates that that the differences between age groups is not statistically significant.
-
-####Create Visualization
-
-```{r}
-t14 <- ggplot(health, aes(x = health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.coworkers.))+geom_bar()+facet_wrap(health$AgeGroup ~., scales="free_y") + ggtitle("Comfort with Discussing Mental Health\nDisorder with Coworkers by Age Group") + xlab("Would you feel comfortable discussing a mental health\ndisorder with your coworkers?") + ylab("Count") + theme(axis.title=element_text(size=12), axis.text=element_text(size=10))
-t14
+#Create subset
+DiscMHCoworkerbyAge <- table(health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.coworkers., health$AgeGroup)
+```
+
+####Crosstab Table
+
+```{r}
+kable(DiscMHCoworkerbyAge)
+```
+
+####Proportions Table
+
+```{r}
+kable(prop.table(DiscMHCoworkerbyAge, 2))
+```
+
+####Chi-Squared
+
+```{r}
+chisq.test(DiscMHCoworkerbyAge)
+```
+
+Our null hypothesis is that there is that reported comfort discussing mental health with coworkers and age are independent.
+Our alternative hypothesis is that there is a relationship between these two variables.
+Because the sensitivity of this test to larger sample sizes we are setting the p value to .01 (Townsley, 2002)
+
+We get a warning that the approximation may be incorrect, likely because because of the small number of respondents in our survey in the 57-77 age group (Townsley, 2002).
+However, the large p value indicates that that the differences in perceived ease of requesting leave between age may not be statistically significant (or we do not have enough information because of the small number of people in the 57-77 age group in our dataset).
+
+####Visualizing the Data
+
+```{r}
+DiscMHCoworkerbyAge_viz <- ggplot(health, aes(x = health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.coworkers.))+geom_bar(fill = "orange")+facet_wrap(health$AgeGroup ~., scales="free_y") + ggtitle("Comfort with Discussing Mental Health\nDisorder with Coworkers by Age Group") + xlab("Would you feel comfortable discussing a mental health\ndisorder with your coworkers?") + ylab("Count") + theme(axis.title=element_text(size=12), axis.text=element_text(size=10))
+DiscMHCoworkerbyAge_viz
 ```
@@
 ```{r}
-MHCbCS <- table(health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.coworkers., health$CompanySize)
-MHCbCS
-#Proportions (as column percentages)
-prop.table(MHCbCS, 2)
+#Create subset
+DiscMHCoworkerbyCompSize <- table(health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.coworkers., health$CompanySize)
+```
+
+####Crosstab Table
+
+```{r}
+#Create crosstab table
+kable(DiscMHCoworkerbyCompSize)
+```
+
+####Proportions Table
+
+```{r}
+#Create proportions table
+kable(prop.table(DiscMHCoworkerbyCompSize, 2))
 ```
@@
 #Chi-Squared (the p value is small)
-chisq.test(MHCbCS)
-```
+chisq.test(DiscMHCoworkerbyCompSize)
+```
+
+Our null hypothesis is that there is that reported comfort discussing mental health with coworkers and age are independent.
+Our alternative hypothesis is that there is a relationship between these two variables.
+Because the sensitivity of this test to larger sample sizes we are setting the p value to .01 (Townsley, 2002)
 
@@
 
-####Create Visualization
-
-```{r}
-t15 <- ggplot(health, aes(x = health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.coworkers.))+geom_bar()+facet_wrap(health$CompanySize ~., scales="free_y") + ggtitle("Comfort with Discussing Mental health\nDisorder with Coworkers by Company Size") + xlab("Would you feel comfortable discussing a mental health\ndisorder with your coworkers?") + ylab("Count") + theme(axis.title=element_text(size=12), axis.text=element_text(size=10))
-t15
+####Visualizing the Data
+
+```{r}
+DiscMHCoworkerbyCompSize_viz <- ggplot(health, aes(x = health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.coworkers.))+geom_bar(fill = "purple")+facet_wrap(health$CompanySize ~., scales="free_y") + ggtitle("Comfort with Discussing Mental health\nDisorder with Coworkers by Company Size") + xlab("Would you feel comfortable discussing a mental health\ndisorder with your coworkers?") + ylab("Count") + theme(axis.title=element_text(size=12), axis.text=element_text(size=10))
+DiscMHCoworkerbyCompSize_viz
 ```
@@
 ```{r}
-MHCbPR <- table(health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.coworkers., health$Have.you.observed.or.experienced.an.unsupportive.or.badly.handled.response.to.a.mental.health.issue.in.your.current.or.previous.workplace.)
-MHCbPR
-```
-
-####Chi-Squared
-
-```{r}
-chisq.test(MHCbPR)
-```
-
-The chi-squared test shows a p value that is less than 0.01.
+#create subset
+DiscMHCoworkerbyPoorResponse <- table(health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.coworkers., health$Have.you.observed.or.experienced.an.unsupportive.or.badly.handled.response.to.a.mental.health.issue.in.your.current.or.previous.workplace.)
+```
+
+####Crosstab Table
+```{r}
+kable(DiscMHCoworkerbyPoorResponse)
+```
+
+####Proportions Table
+```{r}
+kable(prop.table(DiscMHCoworkerbyPoorResponse, 2))
+```
+
+####Chi-Squared
+
+```{r}
+chisq.test(DiscMHCoworkerbyPoorResponse)
+```
+
+Our null hypothesis is that there is that reported comfort discussing mental health with coworkers and experience with a poor response to a mental health issue (current or prior employer) are independent.
+Our alternative hypothesis is that there is a relationship between these two variables.
+Because the sensitivity of this test to larger sample sizes we are setting the p value to .01 (Townsley, 2002)
+
+The chi-squared test shows a p value that is less than .01.
 Therefore, we can reject the null hypothesis (that there is no relationship between these variables).
@@
 
-####Create Visualization
-
-```{r}
-t16 <- ggplot(health, aes(x = health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.coworkers.))+geom_bar()+facet_wrap(health$Have.you.observed.or.experienced.an.unsupportive.or.badly.handled.response.to.a.mental.health.issue.in.your.current.or.previous.workplace.
+####Visualizing the Data
+
+```{r}
+DiscMHCoworkerbyPoorResponse_viz <- ggplot(health, aes(x = health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.coworkers.))+geom_bar(fill="red")+facet_wrap(health$Have.you.observed.or.experienced.an.unsupportive.or.badly.handled.response.to.a.mental.health.issue.in.your.current.or.previous.workplace.
 ~., scales="free_y") + ggtitle("Comfort with Discussing Mental health disorders\nwith Coworkers by Experience with\npoor Workplace Response\nto mental health") + xlab("Would you feel comfortable discussing a mental health\ndisorder with your coworkers?") + ylab("Count") + theme(axis.title=element_text(size=12), axis.text=element_text(size=10))
-t16
+DiscMHCoworkerbyPoorResponse_viz
 ```
@@
 ```{r}
-MHCbCN <- table(health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.coworkers., health$Do.you.think.that.team.members.co.workers.would.view.you.more.negatively.if.they.knew.you.suffered.from.a.mental.health.issue.)
-MHCbCN
-```
-
-####Chi-Squared
-```{r}
-chisq.test(MHCbCN)
-```
-
-The chi-squared is less than .01.  Therefore, we can reject the null and say that there is a relationship between these two variables.
+#Modify Labels for perception of mental health disclosure impact by coworkers
+health$negimpco <- factor(health$Do.you.think.that.team.members.co.workers.would.view.you.more.negatively.if.they.knew.you.suffered.from.a.mental.health.issue.,
+levels = c("Maybe", "No, I don't think they would", "No, they do not", "Yes, I think they would", "Yes, they do"),
+labels = c("Maybe", "No, don't think so", "No, they don't", "Yes, think so", "Yes, they do"))
+#create subset
+DiscMHCoworkerbyNegView <- table(health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.coworkers., health$Do.you.think.that.team.members.co.workers.would.view.you.more.negatively.if.they.knew.you.suffered.from.a.mental.health.issue.)
+```
+
+####Crosstab Table
+
+```{r}
+kable(DiscMHCoworkerbyNegView)
+```
+
+####Proportions Tabale
+
+```{r}
+kable(prop.table(DiscMHCoworkerbyNegView, 2))
+```
+
+####Chi-Squared
+```{r}
+chisq.test(DiscMHCoworkerbyNegView)
+```
+
+Our null hypothesis is that there is that reported comfort discussing mental health with coworkers and experience with a poor response to a mental health issue (current or prior employer) are independent.
+Our alternative hypothesis is that there is a relationship between these two variables.
+Because the sensitivity of this test to larger sample sizes we are setting the p value to .01 (Townsley, 2002).
+The chi-squared is less than .01.
+Therefore, we can reject the null and say that there is a relationship between these two variables.
 
@@
 ```{r}
-t17 <- ggplot(health, aes(x = health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.coworkers.))+geom_bar()+facet_wrap(health$Do.you.think.that.team.members.co.workers.would.view.you.more.negatively.if.they.knew.you.suffered.from.a.mental.health.issue.
-~., scales="free_y") + ggtitle("Comfort with discussing Mental Health Disorder with\n Coworkers by Perceived Negative Impact") + xlab("Would you feel comfortable discussing a mental health\ndisorder with your coworkers?") + ylab("Count") + theme(axis.title=element_text(size=12), axis.text=element_text(size=10))
-t17
+DiscMHCoworkerbyNegView_viz <- ggplot(health, aes(x = health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.coworkers.))+geom_bar(fill = "red")+facet_wrap(health$negimpco ~., scales="free_y") + ggtitle("Comfort with discussing Mental Health Disorder with\n Coworkers by Perceived Negative Impact") + xlab("Would you feel comfortable discussing a mental health\ndisorder with your coworkers?") + ylab("Count") + theme(axis.title=element_text(size=12), axis.text=element_text(size=10))
+DiscMHCoworkerbyNegView_viz
 ```
@@
 
+Townsley, E.R. (2002). Some limitations of chi-square. Retrieved December 6, 2018 from https://www.mtholyoke.edu/courses/etownsle/qr/Chi%20square%20limitations.htm.
+
 Milne, S.
@@
 (1994).
-Factors Influencing Employees???
-Propensity to Use an Employee Assistance Program.
-Personnel Psychology, 47(1), 123???145.
+Factors Influencing Employees Propensity to Use an Employee Assistance Program.
+Personnel Psychology, 47(1), 123-145.
 Retrieved October 24, 2018 from http://search.ebscohost.com.proxy-um.researchport.umd.edu/login.aspx?direct=true&db=bth&AN=9411113184&site=ehost-live

### 2018-12-09 Visualizations/Draft Visualizations Template.Rmd
Added summary and works cited

@@
 
-This is a placeholder for the summary.
+According to the 2010 U.S.
+National Comorbidity Survey, about 18 percent of employed adults have had symptoms of a mental health disorder in the previous month (Harvard Medical School, 2010, para.
+1).
+However, mental health stigma can inhibit people's willingness to seek help (Harvard Medical School, 2010, para.
+2).
+Research on employee resource programs in the workplace targeting mental health/substance abuse issues indicates that conducting outreach to workers on mental health as well as expanding benefits may result in more seeking help for mental health and/or substance abuse issues (Lindrooth, et al, 2005, pp.
+1092, 1102; Lo Sasso, et al, 2006, pp.
+366, 370; Deitz, et al, 2005, p.
+313).
+Benefits could include improved employee mood/health, increased productivity, and lower absenteeism in the workplace (Harvard Medical School, 2010, para.
+28-29; Lo Sasso, Rost, & Beck, 2006, p.
+352).
+
+Our target audience are Human Resources professionals who work for technology companies (or employ technology-focused workers) who are interested in learning more about mental illness in the workplace and are considering expanding wellness programs.
+For our analysis, we used the Open Sourcing Mental Illness dataset.
+The dataset is a 2016 voluntary survey done on mental health in the technology industry (Open Sourcing Mental Illness, LTD, 2016b).
+This dataset allows us to learn more about what mental health disorders are common, what other companies are doing, and how workers view mental health in the workplace.
+For our analysis we only included those who worked for a company (i.e., not self-employed).
+Out of 1,433 total entries, 1,146 were included.
+We cleaned the dataset by standardizing data, as well as correcting typos and formatting errors.
+During our analysis, we shortened some of the labels to make it easier to fit on visualizations and tables.
+
+[INSERT PLOT AND INTERPRETATION OF PLOT HERE]
+
+Based off our analysis, it is clear that a significant number of people in the technology workplace have a mental health disorder.
+This analysis makes it clear that Human Resource professionals who are interested in expanding outreach need to review their policies regarding requesting leave and protection of employee anonymity when they are handling a mental health issue.
+Furthermore, the analysis shows that there is unease among many employees regarding the impact of disclosing a mental health disorder on their career.
+Therefore, it is likely necessary to provide training to employees and supervisors with the goal of reducing stigma around mental health.
 
@@
 For the presentation, I created a template for the presentation that included what was needed and placeholder slides for the analyses the group did.
-I also did slides related to my analysis (anonymity policies, ease of taking leave, comfort discussing with coworkers and supervisors) and used the findings to draft some recommendations.For the final package, I did the first draft of the summary.
+I also did slides related to my analysis (anonymity policies, ease of taking leave, comfort discussing with coworkers and supervisors) and used the findings to draft some recommendations.For the final package, I did the first draft of the summary as well as revised and cleaned up the analyses that I worked on.
 
@@
 
-Townsley, E.R. (2002). Some limitations of chi-square. Retrieved December 6, 2018 from https://www.mtholyoke.edu/courses/etownsle/qr/Chi%20square%20limitations.htm.
+Deitz, D., Cook, R., & Hersch, R.
+(2005).
+Workplace Health Promotion and Utilization of Health Services: Follow-up Data Findings.
+The Journal of Behavioral Health Services & Research, 32(3), 306-319.
+Retrieved October 21, 2018 from https://doi-org.proxy-um.researchport.umd.edu/10.1007/BF02291830
+
+Harvard Medical School (2010).
+Mental health problems in the workplace [Newsletter].
+Retrieved December 8, 2018, from https://www.health.harvard.edu/newsletter_article/mental-health-problems-in-the-workplace.
+
+Lo Sasso, A.
+T., Lindrooth, R.
+C., Lurie, I.
+Z., & Lyons, J.
+S.
+(2006).
+Expanded Mental Health Benefits and Outpatient Depression Treatment Intensity.
+Medical Care, 44(4), 366-372.
+Retrieved October 21, 2018 from https://doi-org.proxy-um.researchport.umd.edu/10.1097/01.mlr.0000204083.55544.f8
+
+Lindrooth, R.
+C., Lo Sasso, A.
+T., & Lurie, I.
+Z.
+(2005).
+The Effect of Expanded Mental Health Benefits on Treatment Initiation and Specialist Utilization.
+Health Services Research, 40(4), 1092-1107.
+Retrieved October 21, 2018 from https://doi-org.proxy-um.researchport.umd.edu/10.1111/j.1475-6773.2005.00406.x
+
+Lo Sasso, A.
+T., Rost, K., & Beck, A.
+(2006).
+Modeling the Impact of Enhanced Depression Treatment on Workplace Functioning and Costs: A Cost-Benefit Approach.
+Medical Care, 44(4), 352-358.
+Retrieved October 21, 2018 from https://doi-org.proxy-um.researchport.umd.edu/10.1097/01.mlr.0000204049.30620.1e
 
@@
 Retrieved October 24, 2018 from http://search.ebscohost.com.proxy-um.researchport.umd.edu/login.aspx?direct=true&db=bth&AN=9411113184&site=ehost-live
+
+Open Sourcing mental Illness, LTD (2016a). OSMI (Version 1) [Data file]. Retrieved September 7, 2018, from https://osmihelp.org/research
+
+Open Sourcing Mental Illness, LTD (2016b). osmi-survey-2016_1479139902 [Metadata File]. Retrieved September 19, 2018, from https://osmihelp.org/research.
+
+Townsley, E.R. (2002). Some limitations of chi-square. Retrieved December 6, 2018 from https://www.mtholyoke.edu/courses/etownsle/qr/Chi%20square%20limitations.htm.

### 2018-12-13 Visualizations/Draft Visualizations Template.Rmd
Finished summary.

@@
 
-[INSERT PLOT AND INTERPRETATION OF PLOT HERE]
-
-Based off our analysis, it is clear that a significant number of people in the technology workplace have a mental health disorder.
+One plot we used in our analysis is the Distribution of Mental health disorders that respondents to the survey had.
+The visualization and the description of results can also be found in the "Distribution of Mental health disorders" subheading of Section 1.
+
+```{r}
+p+xlab("Current Mental health disorders")+ggtitle("Distribution of Mental health disorders currently")
+```
+
+As indicated above, mood disorder and anxiety disorder are the most common in our analysis.
+Furthermore, it is clear that a significant number of people who responded to the survey have at least one mental health disorder.
 This analysis makes it clear that Human Resource professionals who are interested in expanding outreach need to review their policies regarding requesting leave and protection of employee anonymity when they are handling a mental health issue.
@@
 #Who did what in the project
+
+Monalisa -
 
@@
 I also did slides related to my analysis (anonymity policies, ease of taking leave, comfort discussing with coworkers and supervisors) and used the findings to draft some recommendations.For the final package, I did the first draft of the summary as well as revised and cleaned up the analyses that I worked on.
+
+Shruti -
 

### 2018-12-13 Visualizations/Draft Visualizations Template.Rmd
Corrected anon policies by company size visualization
X axis label was wrong

@@
   geom_bar(stat = 'identity', position = 'dodge', alpha = 2/3) +              
-  labs(x = NULL, y = 'Proportion', fill = 'Gender')+ggtitle('Distribution of mental health status among genders (1)')
+  labs(x = NULL, y = 'Proportion', fill = 'Gender')+ggtitle('Distribution of mental health status among genders')
 ```
@@
   geom_bar(stat = 'identity', position = 'dodge', alpha = 2/3) +              
-  labs(x = NULL, y = 'Proportion', fill = 'Disorder')+ggtitle('Distribution of mental health status among genders (2)')
+  labs(x = NULL, y = 'Proportion', fill = 'Disorder')+ggtitle('Distribution of mental health status among genders')
 ```
@@
   geom_bar(stat = 'identity', position = 'dodge', alpha = 2/3) +              
-  labs(x = "Age Groups", y = 'Proportion', fill = 'Disorder')+ggtitle('Distribution of mental health status based on age groups (1)')
+  labs(x = "Age Groups", y = 'Proportion', fill = 'Disorder')+ggtitle('Distribution of mental health status based on age groups')
 ```
@@
   geom_bar(stat = 'identity', position = 'dodge', alpha = 2/3) +              
-  labs(x = "Disorder", y = 'Proportion', fill = 'Age group')+ggtitle('Distribution of mental health status based on age groups (2)')
+  labs(x = "Disorder", y = 'Proportion', fill = 'Age group')+ggtitle('Distribution of mental health status based on age groups')
 ```
@@
 #Create visualization
-AnoymityPolicies_By_CompanySize_Viz <- ggplot(health, aes(x = health$AnonPolicies2))+geom_bar(fill="purple")+facet_wrap(~health$CompanySize, scales="free_y") + ggtitle("Anonymity Protections by Comapny Size") + xlab("Perceived Difficulty Level") + ylab("Count")+ theme(axis.title=element_text(size=12))
+AnoymityPolicies_By_CompanySize_Viz <- ggplot(health, aes(x = health$AnonPolicies2))+geom_bar(fill="purple")+facet_wrap(~health$CompanySize, scales="free_y") + ggtitle("Anonymity Protections by Comapny Size") + xlab("Is your anonymity protected?") + ylab("Count")+ theme(axis.title=element_text(size=12))
 AnoymityPolicies_By_CompanySize_Viz
@@
 
-Shruti -
+Shruti - Collaborated with the team members to decide upon work plan and the tasks.
+For data cleaning, I examined nine variables for any issues.
+Worked on the age variable where I replaced the meaningless ages like 3, 110 with the average age.
+I exmained all the answers to the gender variable as they were subjective responses and divided them into Male, Female and others accordingly.
+For the descriptive analysis, I worked with the nine variables using summary and tables.
+For the visualization and plotting, I worked on the distribution of mental disorder.
+I analysed the responses to come up with a way to split it.
+For instance, the responses were of the format - Anxiety Disorder (Generalized, Social, Phobia, etc)|Mood Disorder (Depression, Bipolar Disorder, etc), I split them and separated them using R code to just the higher categories like anxiety Disorder, Mood Disorder to visualise it.
+For ease of visualisations using age, I created age groups (17-37, 37-57 etc).
+I visualised the distribution of mental illness across gender and age.
+I also did the visualisation and interpretations on negative consequences on discussing physical vs mental disorders.
+I documented my parts in the R markdown file.
+I worked on my parts for the presentation.
+For final package, I cleaned up the analaysis and visualizations that I worked on as well.
 

### 2018-12-13 Final /Draft Visualizations Template.Rmd
Final package chnages

--- 2018-12-13 Visualizations/Draft Visualizations Template.Rmd
@@
 #Create visualization
-AnoymityPolicies_By_CompanySize_Viz <- ggplot(health, aes(x = health$AnonPolicies2))+geom_bar(fill="purple")+facet_wrap(~health$CompanySize, scales="free_y") + ggtitle("Anonymity Protections by Comapny Size") + xlab("Is your anonymity protected?") + ylab("Count")+ theme(axis.title=element_text(size=12))
+AnoymityPolicies_By_CompanySize_Viz <- ggplot(health, aes(x = health$AnonPolicies2))+geom_bar(fill="purple")+facet_wrap(~health$CompanySize, scales="free_y") + ggtitle("Anonymity Protections by Comapny Size") + xlab("Perceived Difficulty Level") + ylab("Count")+ theme(axis.title=element_text(size=12))
 AnoymityPolicies_By_CompanySize_Viz

### 2018-12-13 Final /Draft Visualizations Template.Rmd
Pushing changes

@@
   geom_bar(stat = 'identity', position = 'dodge', alpha = 2/3) +              
-  labs(x = "Age Groups", y = 'Proportion', fill = 'Disorder')+ggtitle('Distribution of mental health status based on age groups')
+  labs(x = "Age Groups", y = 'Proportion', fill = 'Disorder')+ggtitle('Distribution of mental health status across age groups')
 ```
@@
   geom_bar(stat = 'identity', position = 'dodge', alpha = 2/3) +              
-  labs(x = "Disorder", y = 'Proportion', fill = 'Age group')+ggtitle('Distribution of mental health status based on age groups')
+  labs(x = "Disorder", y = 'Proportion', fill = 'Age group')+ggtitle('Distribution of mental health status across age groups')
 ```

### 2018-12-14 Final /FinalReport.Rmd
Final report changes
Pushing individual ontribution of mona
As her github stopped working, it was pushed from my system

--- 2018-12-13 Final /Draft Visualizations Template.Rmd
@@
 ---
-title: "Final Report Semester Project"
+title: "Final Report: The need for mental health outreach in the workplace"
 output:
@@
 
-Monalisa -
+Monalisa - In the initial stage, I collaborated with the team to do prelimnary research in the area of mental health and create the work plan.
+I came up with about 9 research questions that we could analyze using the dataset.
+(We all did some brainstorming with all suggested questions and shortlisted 15 questions for the analysis).
+For the data cleaning phase, I examined and cleaned 10 variables.
+For the R Script, I collaborated with the team to understand what kind of tests we can run with the variables and what questions can be answered by doing so.
+I was assigned 5 questions that helped gain insights into the number of employers in the dataset who provided mental health benefits to the employees, if they formally discussed these policies and questions that answered employee perception of negative consequences of discussing mental health at previous and current workplace.
+I did statistical tests (Chi-squared and Crammer's V) to conclude that a relationship exists between the two variables.
+As all my variables were categorical, I used barplots, ggplots and Chi-squared tests to perform visualizations and to test relationships respectively.
+For the presentation, I again collaborated with the team and created slides for my part of the analysis.
+Lastly, I cleaned my part of the code based on the feedback received.
 
